### 2019-06-23 paper/figures/fem.tex
First section.

\begin{table}[hbpt]
    \caption{Absorbing Panel or Panel and Temporal Indicators}
    \label{withinres}
    \begin{tabularx}{\textwidth}{Y Y c c c c c c}
    \toprule
    Model & Parameter & \multicolumn{2}{c}{Econometrics.jl} & \multicolumn{2}{c}{Stata (reghdfe)} & \multicolumn{2}{c}{R (plm)} \\
    \midrule
    \multirow{4}{*}{Within PID} & Intercept & 0.0274 & 0.0355 & 0.0274 & 0.0355 &  &  \\
    & PrbConv & -0.0004 & 0.0004 & -0.0004 & 0.0004 & -0.0004 & 0.0004 \\
    & AvgSen & -0.0002 & 0.0003 & -0.0002 & 0.0003 & -0.0002 & 0.0003 \\
    & PrbPris & -0.0093 & 0.0066 & -0.0093 & 0.0066 & -0.0093 & 0.0066 \\
    \midrule
    \multirow{4}{*}{Within PTID} & Intercept & 0.0279 & 0.0360 & 0.0279 & 0.0360 &  &  \\
    & PrbConv & -0.0003 & 0.0005 & -0.0003 & 0.0005 & -0.0003 & 0.0005 \\
    & AvgSen & -0.0004 & 0.0002 & -0.0004 & 0.0002 & -0.0004 & 0.0002 \\
    & PrbPris & -0.0070 & 0.0089 & -0.0070 & 0.0089 & -0.0069 & 0.0089 \\
    \bottomrule
    \end{tabularx}
\end{table}

### 2019-06-23 paper/paper.tex
First section.

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

%%%
%% Language Support
%%%
\usepackage[english]{babel}
\usepackage{csquotes}

%%%
%% Images
%%%
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage[export]{adjustbox}

%%%
%% Fonts and Typewriting
%%%
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{bm}

%%%
%% Enhances Figures and Tables environments
%%%
\usepackage{placeins}
\usepackage[hypcap=true]{caption}
\usepackage{booktabs, multirow, array, tabularx, floatrow, cellspace, threeparttable}
\floatsetup[table]{capposition = top}
\newcolumntype{Z}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\renewcommand{\arraystretch}{1.25}

%%%
%% Enables hyperlinks
%%%
\usepackage{varioref}
\hypersetup{
    pdftitle    = {Econometrics.jl},
    pdfsubject  = {JuliaCon 2019 Proceedings},
    pdfauthor   = {José Bayoán Santiago Calderón},
    pdfkeywords = {Julia, Econometrics, Statistical Software, Software Validation},
    colorlinks  = true,
    linkcolor   = black,
    filecolor   = black,
    urlcolor    = black,
    citecolor   = black
}
\urlstyle{same}

%%%
%% Cross References
%%%
\usepackage{cleveref}

\begin{document}

\input{header}

\maketitle

\begin{abstract}

Econometrics.jl is a package for econometrics analysis. It provides a series of most common routines for applied econometrics such as models for continuous, nominal, and ordinal outcomes, longitudinal estimators, variable absorption, weights, rank deficient, and robust variance covariance estimators.

\end{abstract}

\section{Introduction}

Software to economists is what hammers are to blacksmiths. As scientists, the tools to work with data are as important as the know-how to perform the analysis. A requirement for good science is that the tools used in the process have a certain standard in terms of quality, transparency, and flexibility. The analysis must allow for the process to be verifiable and replicable.

This study will: (1) provide an overview of common routines and their statistical and technical requirements, (2) provide an overview of tools available with their peculiarities, (3) discuss design decisions in the development of these tools, and (4) showcase \textit{Econometrics.jl} as a new tool for applied work.

Regression models may be used for several purposes. These may provide a basis for prediction models, causal inference, etc. Common targets include confidence intervals of the parameters estimates, joint-significance of a feature, out-of-sample predictive performance, and others. In other words, obtaining the estimates of a model is usually only part of the task. In order to judge a model, one may require to perform diagnostics and tests to justify potential conclusions for an analysis.

Regression analysis is at the core of applied econometrics. It can be challenging to grasp the extent what makes up the broad term of regression analysis. The following describes a very brief survey of what this technique might entail. Regression analysis can be used for both observational and experimental settings and it allows great flexibility for a multitude of applications. The main idea is to find estimates for model parameters to optimize some objective such as the likelihood in maximum likelihood estimation (MLE). Other potential objectives include restricted maximum likelihood (REML) or a Bayesian approach such as maximum a posteriori probability (MAP). One framework is the generalized linear model (GLM) which use a linear predictor that is mapped through a link function to a distribution modeling the response. Continuous responses might use a Normal distribution, count responses a log link with a Negative Binomial distribution, and probability models might use a categorical distribution with links that map to valid probabilities such as the Logit link. In cases such as probability models where the responses are multidimensional, the generalization is known as vector generalized linear models (VGLM). Other generalizations include relaxing the relation between the linear predictor and the outcome to be the sum of smoothing functions through a generalized additive model (GAM) framework or incorporating random effects through a mixed models approach. Some estimators address challenges such as endogeneity, censored responses, and zero-inflated responses through various solutions such as instrumental variables or censored regression model. Others, exploit aspects of the data to overcome challenges or increase efficiency such as random effects in longitudinal data. In relation to the second moment of the estimator, robust variance covariance estimators or boostrapping may be required for inference.

Out of the many potential tools practitioners may require, what are some of the most common? Not every estimator is as widely accessible or commonly used. Some educated guesses may be well justified such as ordinary least squares being more widely used than spatially-weighted regressions. In order to avoid speculation, I defer to a reasonable assumption that the most common estimators are those usually taught in academic programs and available in widely used software similarly to \cite{Renfro_2009}. Most programs teach tools to address the most common response types: continuous, count, rates, nominal, and ordinal outcomes. Hence, some routines might be linear models, Poisson/negative binomial, multinomial logistic regression, and ordinal logistic regression with proportional odds assumption. Topics in time series and panel data are usually offered in most programs. Perhaps the most common topic is short panels (many units of observations through relatively small number of repeated observations). Common estimators include pooling, first-difference, fixed effects / within estimator, and one-way random effects. The between estimator is usually masked as an intermediate model for estimating the error component in the random effects model. Lastly, the two big challenges taught in most programs are endogeneity and heteroscedasticity. These challenges are usually countered through instrumental variables (e.g., 2SLS) or robust variance-covariance estimators (e.g., heteroscedasticity consistent estimators).

\cite{Renfro_2009} surveyed the functionality of 24 alternatives for common econometrics routines. Throughout the history of econometrics software, alternatives have risen and fallen in following. Some high contenders by market share include Stata \cite{Stata}, R \cite{R}, MATLAB, Python \cite{Python}, IBM SPSS Statistics, SAS software, and EViews. These include both commercial and open-source alternatives. Functionality may be provided by the base/standard libraries in the statistical software environment, as a product such as a toolkit or user contributed such as a module/package that is distributed. Some examples of user-contributed functionality include the \textit{reghdfe} Stata module and a series of R packages such as \textit{MASS} \cite{MASS}, \textit{lmtest} \cite{lmtest}, \textit{sandwich} \cite{sandwich}, \textit{plm} \cite{plm}, and \textit{mlogit} \cite{mlogit}.

The Julia language \cite{Julia} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks. The following sections describe commons estimators, the Julia ecosystem supporting tools, and Econometrics.jl which provides further functionality.

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb \ref ) in order to
protect against late changes of order, etc.

\section{USING THE JuliaCon Article CLASS FILE}

If the file \verb juliacon.cls  is not already in the appropriate system directory
for \LaTeX{} files, either arrange for it to be put there or copy
it to your working directory. The \verb juliacon  document class is implemented
as a complete class, not a document style option. In order to
use the \verb juliacon  document class, replace \verb article  by \verb juliacon  in the
\verb \documentclass  command at the beginning of your document:
\vskip 6pt
\begin{centering}
    \verb \documentclass{article}  \end{centering}
\vskip 6pt
replace by
\vskip 6pt
 \verb \documentclass{juliacon}  \vskip 6pt
In general, the following standard document \verb style  options should
{ \itshape not} be used with the {\footnotesize \itshape article} class file:
\begin{enumerate}
\item[(1)] \verb 10pt,  \verb 11pt,  \verb 12pt   ? unavailable;
\item[(2)] \verb twoside  (no associated style file) ? \verb twoside  is the default;
\item[(3)] \verb fleqn, \verb leqno, \verb titlepage ? should not be used;
\end{enumerate}

\section{Additional Document Style Options}
\label{sec:additional_doc}
%
The following additional style option is available with the \verb juliacon  class file:
\vskip 6pt
Please place any additional command definitions at the very start of
the \LaTeX{} file, before the \verb \begin{document} . For example, user-defined
\verb \def  and \verb \newcommand   commands that define macros for
technical expressions should be placed here. Other author-defined
macros should be kept to a minimum.
\vskip 6pt
Commands that differ from the standard \LaTeX{} interface, or that
are provided in addition to the standard interface, are explained in
this guide. This guide is not a substitute for the \LaTeX{} manual itself.
Authors planning to submit their papers in \LaTeX{} are advised to use
\verb \juliacon.cls  as early as possible in the creation of their files.

%
%
%
%
\begin{table*}[t]
\tabcolsep22pt
\tbl{If necessary, the tables can be extended both columns.}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\label{tab:symbols}
\begin{tabnote}
This is an example of table footnote.
\end{tabnote}
\end{table*}
% \begin{figure*}[t]
% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
% \caption{If necessary, the images can be extended both columns.}
%   \label{fig:sample_image}
% \end{figure*}

\section{Additional features}
\label{sec:additional_faci}
In addition to all the standard \LaTeX{} design elements, the \verb juliacon  class file includes the following features:
In general, once you have used the additional \verb juliacon.cls facilities
in your document, do not process it with a standard \LaTeX{} class
file.

\subsection{Titles, Author's Name, and Affiliation}
\label{subsub:title_auth}
The title of the article, author's name, and affiliation are used at the
beginning of the article (for the main title). These can be produced
using the following code:

\begin{verbatim}
\title{ This is an example of article title} }
\author{
   \large 1st Author \\[-3pt]
   \normalsize 1st author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	1st author's email address \\[-3pt]
  \and
   \large 2nd Author \\[-3pt]
   \normalsize 2nd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	2nd author's email address \\[-3pt]
\and
   \large 3rd Author \\[-3pt]
   \normalsize 3rd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	3rd author's email address \\[-3pt]
}
\maketitle
\end{verbatim}

\subsection{Writing Julia code}

A special environment is already defined for Julia code,
built on top of \textit{listings} and \textit{jlcode}.

\begin{verbatim}
\begin{lstlisting}[language = Julia]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[language = Julia]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}

\subsection{Abstracts, Key words, term etc...}
\label{subsub:abs_key_etc}

At the beginning of your article, the title should be generated
in the usual way using the \verb \maketitle  command. For genaral tem and keywords use
\verb \terms ,
\verb \keywords  commands respectively. The abstract should be enclosed
within an abstract environment, All these environment
can be produced using the following code:
\begin{verbatim}
\terms{Experimentation, Human Factors}

\keywords{Face animation, image-based modelling...}

\begin{abstract}
In this paper, we propose a new method for the
systematic determination of the model's base of
time varying delay system. This method based on
the construction of the classification data related
to the considered system. The number, the orders,
the time delay and the parameters of the local
models are generated automatically without any
knowledge about the full operating range of the
process. The parametric identification of the local
models is realized by a new recursive algorithm for
on line identification of systems with unknown time
delay. The proposed algorithm allows simultaneous
estimation of time delay and parameters of
discrete-time systems. The effectiveness of
the new method has been illustrated through
simulation.
\end{abstract}

\end{verbatim}

\section{Some guidelines}
\label{sec:some_guide}
The following notes may help you achieve the best effects with the
\verb juliacon  class file.

\subsection{Sections}
\label{subsub:sections}
\LaTeXe{}  provides four levels of section headings and they are all
defined in the \verb juliacon  class file:
\begin{itemize}
\item \verb \section   \item \verb \subsection  \item \verb \subsubsection  \item \verb \paragraph  \end{itemize}
Section headings are automatically converted to allcaps style.
\subsection{Lists}
\label{sec:lists}
%
The \verb juliacon   class file provides unnumbered lists using the
\verb unnumlist  environment for example,

\begin{unnumlist}
\item First unnumbered item which has no label and is indented from the
left margin.
\item Second unnumbered item.
\item Third unnumbered item.
\end{unnumlist}
The unnumbered list which has no label and is indented from the
left margin. was produced by:
\begin{verbatim}
\begin{unnumlist}
\item First unnumbered item...
\item Second unnumbered item...
\item Third unnumbered item...
\end{unnumlist}
\end{verbatim}

The \verb juliacon   class file also provides hyphen list using the
\verb itemize  environment for example,
\begin{itemize}
\item First unnumbered bulleted item which has no label and is indented
from the left margin.
\item Second unnumbered bulleted item.
\item Third unnumbered bulleted item which has no label and is indented
from the left margin.
\end{itemize}
was produced by:
\begin{verbatim}
\begin{itemize}
\item First item...
\item Second item...
\item Third item...
\end{itemize}
\end{verbatim}

Numbered list is also provided in acmtog class file using the
enumerate environment for example,
\begin{enumerate}
\item The attenuated and diluted stellar radiation.
\item Scattered radiation, and
\item Reradiation from other grains.
\end{enumerate}

was produced by:
\begin{verbatim}
\begin{enumerate}
\item The attenuated...
\item Scattered radiation, and...
\item Reradiation from other grains...
\end{enumerate}
\end{verbatim}
\subsection{Illustrations (or figures)}
\label{subsub:sec_Illus}
The \verb juliacon   class file will cope with most of the positioning of
your illustrations and you should not normally use the optional positional
qualifiers on the \verb figure   environment that would override
these decisions.
\vskip 6pt

%
\begin{figure}[t]
\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
\caption{This is example of the image in a column.}
	\label{fig:sample_figure}
\end{figure}

The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
organization \footnote{https://github.com/JuliaGraphs}.

Figure captions should be \emph{below} the figure itself, therefore the
\verb \caption  command should appear after the figure or space left for
an illustration. For example, Figure 1 is produced using the following
commands:

\begin{verbatim}
\begin{figure}
\centerline{\includegraphics[width=20pc]{Graphics.eps}}
\caption{An example of the testing process for a
binary tree. The globa null hypothesis is tested
first at level $\alpha$ (a), and the level of
individual variables is reached last (d). Note
that individual hypotheses can be tested at
level $\alpha/4$ and not $\alpha/8$ as one might
expect at first.}
\label{sample-figure_2}
\end{figure}
\end{verbatim}
Figures can be resized using first and second argument of
\verb \includegraphics   command. First argument is used for modifying
figure height and the second argument is used for modifying
figure width respectively.
\vskip 6pt
Cross-referencing of figures, tables, and numbered, displayed
equations using the \verb \label  and \verb \ref   commands is encouraged.
For example, in referencing Figure 1 above, we used
\verb Figure~\ref{sample-figure}   \subsection{Tables}
\label{subsub:sec_Tab}
The \verb juliacon   class file will cope with most of the positioning of
your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
decisions. Table captions should be at the top.
\begin{verbatim}
\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Train70 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test70 & Testing Data I & & 105\\\hline
Test30 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}\end{verbatim}

\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\subsection{Landscaping Pages}
\label{subsub:landscaping_pages}
If a table is too wide to fit the standard measure, it may be turned,
with its caption, to 90 degrees. Landscape tables cannot be produced
directly using the \verb juliacon   class file because \TeX{} itself cannot
turn the page, and not all device drivers provide such a facility.
The following procedure can be used to produce such pages.
\vskip 6pt
Use the package \verb rotating   in your document and change the coding
from
\begin{verbatim}
\begin{table}...\end{table}
to
\begin{sidewaystable}...\end{sidewaystable}
and for figures
\begin{figure}...\end{figure}
to
\begin{sidewaysfigure}...\end{sidewaysfigure}
\end{verbatim}

environments in your document to turn your table on the appropriate
page of your document. For instance, the following code prints
a page with the running head, a message half way down and the
table number towards the bottom.
\begin{verbatim}
\begin{sidewaystable}
\tbl{Landscape table caption to go here.}{...}
\label{landtab}
\end{sidewaystable}
\end{verbatim}

\subsection{Double Column Figure and Tables}
\label{subsub:double_fig_tab}
For generating the output of figures and tables in double column
we can use the following coding:

\begin{enumerate}
\item For Figures:
\begin{verbatim}
\begin{figure*}...\end{figure*}
\end{verbatim}
\item For landscape figures:
\begin{verbatim}
\begin{sidewaysfigure*}...\end{sidewaysfigure*}
\end{verbatim}
\item For Tables:
\begin{verbatim}
\begin{table*}...\end{table*}
\end{verbatim}
\item For landscape tables:
\begin{verbatim}
\begin{sidewaystable*}...\end{sidewaystable*}
\end{verbatim}
\end{enumerate}

\subsection{Typesetting Mathematics}
\label{subsub:type_math}
The \verb juliacon class file will set displayed mathematics with center to
the column width, provided that you use the \LaTeXe{} standard of
open and closed square brackets as delimiters.
The equation
\[
\sum_{i=1}^p \lambda_i = (S)
\]

was typeset using the acmtog class file with the commands

\begin{verbatim}
\[
\sum_{i=1}^p \lambda_i = (S)
\]
\end{verbatim}

For display equations, cross-referencing is encouraged. For example,
\begin{verbatim}
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.
\end{verbatim}
The following output is generated with the above coding:
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.

\subsection{Enunciations}
\label{subsub:enunciation}
The \verb juliacon   class file generates the enunciations with the help of
the following commands:
\begin{verbatim}
\begin{theorem}...\end{theorem}
\begin{strategy}...\end{strategy}
\begin{property}...\end{property}
\begin{proposition}...\end{proposition}
\begin{lemma}...\end{lemma}
\begin{example}...\end{example}
\begin{proof}...\end{proof}
\begin{definition}...\end{definition}
\begin{algorithm}...\end{algorithm}
\begin{remark}...\end{remark}
\end{verbatim}
The above-mentioned coding can also include optional arguments
such as
\begin{verbatim}
\begin{theorem}[...]. Example for theorem:
\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven ... created equal.
\end{theorem}
\end{verbatim}

\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven years ago our fathers brought forth,
upon this continent, a new nation, conceived in Liberty,
 and dedicated to the proposition that all men are
created equal.
\end{theorem}

\subsection{Extract}
\label{subsub:extract}
Extract environment should be coded within
\begin{verbatim}
\begin{extract}..\end{extract}
\end{verbatim}

\subsection{Balancing column at last page}
\label{subsub:Balance}
For balancing the both column length at last page use :
\begin{verbatim}
\vadjust{\vfill\pagebreak}
\end{verbatim}

%\vadjust{\vfill\pagebreak}

at appropriate place in your \TeX{} file or in bibliography file.

\section{Handling references}
\label{subsub:references}
References are most easily (and correctly) generated using the
BIBTEX, which is easily invoked via
\begin{verbatim}
\bibliographystyle{juliacon}
\bibliography{ref}
\end{verbatim}
When submitting the document source (.tex) file to external
parties, the ref.bib file should be sent with it.
\cite{bezanson2017julia}

\input{bib.tex}

\end{document}

% Inspired by the International Journal of Computer Applications template

### 2019-06-24 paper/paper.tex
Updates from Overleaf

@@
 \usepackage{bm}
+\usepackage{microtype}
 
@@
 \usepackage[hypcap=true]{caption}
+%\captionsetup[table]{labelfont=bf,textfont=it}
+%\captionsetup[figure]{labelfont=bf,textfont=it}
 \usepackage{booktabs, multirow, array, tabularx, floatrow, cellspace, threeparttable}
@@
 
-%%%
-%% Cross References
-%%%
-\usepackage{cleveref}
-
 \begin{document}
@@
 
+% An abstract with at most 600 characters, written in plain English with no symbol nor formula.
+% A list of at most 10 keywords as specified in the template, separated by commas and written in plain English.
+% Compared to an extended abstract, a full paper presents more of the background and context motivating the work.
+It compares the work to other approaches taken in the field and gives some additional insights on the talk.
+Use cases back up the work by showing how it can be used.
+
 Econometrics.jl is a package for econometrics analysis.
@@
 \section{Introduction}
-
-Software to economists is what hammers are to blacksmiths.
-As scientists, the tools to work with data are as important as the know-how to perform the analysis.
-A requirement for good science is that the tools used in the process have a certain standard in terms of quality, transparency, and flexibility.
-The analysis must allow for the process to be verifiable and replicable.
 
@@
 
-The Julia language \cite{Julia} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks.
+The Julia language \cite{Bezanson_Edelman_Karpinski_Shah_2017} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks.
 The following sections describe commons estimators, the Julia ecosystem supporting tools, and Econometrics.jl which provides further functionality.
 
-\section{The JuliaCon Article Class}
-\label{sec:documentclass}
-%
-The juliacon class file preserves the standard LATEX{} interface such
-that any document that can be produced using the standard LATEX{}
-article class can also be produced with the class file.\vskip 6pt
-It is likely that the make up will change after file submission. For
-this reason, we ask you to ignore details such as slightly long lines,
-page stretching, or figures falling out of synchronization, as these
-details can be dealt with at a later stage.\vskip 6pt
-Use should be made of symbolic references (\verb \ref ) in order to
-protect against late changes of order, etc.
+\section{Common Estimators}
 
-\section{USING THE JuliaCon Article CLASS FILE}
+\subsection{Weighted Least Squares}
 
-If the file \verb juliacon.cls  is not already in the appropriate system directory
-for \LaTeX{} files, either arrange for it to be put there or copy
-it to your working directory. The \verb juliacon  document class is implemented
-as a complete class, not a document style option. In order to
-use the \verb juliacon  document class, replace \verb article  by \verb juliacon  in the
-\verb \documentclass  command at the beginning of your document:
-\vskip 6pt
-\begin{centering}
-    \verb \documentclass{article}  \end{centering}
-\vskip 6pt
-replace by
-\vskip 6pt
- \verb \documentclass{juliacon}  \vskip 6pt
-In general, the following standard document \verb style  options should
-{ \itshape not} be used with the {\footnotesize \itshape article} class file:
-\begin{enumerate}
-\item[(1)] \verb 10pt,  \verb 11pt,  \verb 12pt   ? unavailable;
-\item[(2)] \verb twoside  (no associated style file) ? \verb twoside  is the default;
-\item[(3)] \verb fleqn, \verb leqno, \verb titlepage ? should not be used;
-\end{enumerate}
+Weighted least squares solves
 
-\section{Additional Document Style Options}
-\label{sec:additional_doc}
-%
-The following additional style option is available with the \verb juliacon  class file:
-\vskip 6pt
-Please place any additional command definitions at the very start of
-the \LaTeX{} file, before the \verb \begin{document} . For example, user-defined
-\verb \def  and \verb \newcommand   commands that define macros for
-technical expressions should be placed here. Other author-defined
-macros should be kept to a minimum.
-\vskip 6pt
-Commands that differ from the standard \LaTeX{} interface, or that
-are provided in addition to the standard interface, are explained in
-this guide. This guide is not a substitute for the \LaTeX{} manual itself.
-Authors planning to submit their papers in \LaTeX{} are advised to use
-\verb \juliacon.cls  as early as possible in the creation of their files.
+\begin{equation}
+	\beta = \left(X^{\top} W X\right)^{-1} X^{\top} W y
+\end{equation}
+with information matrix
+\begin{equation}
+\Psi = \left(X^{\top} W X\right)^{-1}
+\end{equation}
 
-%
-%
-%
-%
-\begin{table*}[t]
-\tabcolsep22pt
-\tbl{If necessary, the tables can be extended both columns.}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Test 1 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test 2 & Testing Data I & & 105\\\hline
-Test 3 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\label{tab:symbols}
-\begin{tabnote}
-This is an example of table footnote.
-\end{tabnote}
-\end{table*}
-% \begin{figure*}[t]
-% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
-% \caption{If necessary, the images can be extended both columns.}
-%   \label{fig:sample_image}
-% \end{figure*}
+where $X$ is the full rank version of a model matrix, $W$ a diagonal matrix with positive values (e.g., frequency), and $y$ the response.
+The common solution method is to factorize $X$ as either its QR decomposition or Cholesky decomposition.
+Singular value decomposition may also be used, but it is rare as the computational complexity is significantly higher.
+In the case of the QR decomposition the solution method comes down to, transforming the model matrix and the response by row-wise multiplying them by the square root of the weights.
+Afterwards, the factorization is used to solve the system of equations using the appropriate method.
+In the case of a QR decomposition, $R$ is an upper triangular matrix which enables back substitution to obtain the solution efficiently without matrix inversion.
+However, a Cholesky decomposition would still be required if the information matrix is desired.
+The solution method with QR decomposition is delineated in equation \ref{QR}.\footnote{The \textbackslash refers multiplication of $b$ by the inverse of $A$ on the left}
 
-\section{Additional features}
-\label{sec:additional_faci}
-In addition to all the standard \LaTeX{} design elements, the \verb juliacon  class file includes the following features:
-In general, once you have used the additional \verb juliacon.cls facilities
-in your document, do not process it with a standard \LaTeX{} class
-file.
+The case for the Cholesky decomposition follows closely and without loss of generality other variants could be used such as Bunch-Kaufman decomposition or the upper triangular form ($U^{\top}U$).
+The QR decomposition is more numerically stable, but more expensive than Cholesky.\footnote{$\mathcal{O}\left(n^{3}\right) > \mathcal{O}\left(2mn^{2}-\frac{2}{3}2n^{3}\right)$ where the matrix has $m$ rows and $n$ columns}.
+Equation \ref{Cholesky} delineates the solution method with Cholesky decomposition.
+Since the information matrix is an important component, Bunch-Kaufman decomposition, a Cholesky variant, is the preferred method used in \textit{Econometrics.jl}.
 
-\subsection{Titles, Author's Name, and Affiliation}
-\label{subsub:title_auth}
-The title of the article, author's name, and affiliation are used at the
-beginning of the article (for the main title). These can be produced
-using the following code:
+\begin{equation}
+\label{QR}
+\begin{split}
+	\tilde{X} = X .* \sqrt{w} \\
+	\tilde{y} = y .* \sqrt{w} \\
+	QR = \tilde{X} \\
+	\beta = R \ \backslash \ \left( Q^{\top} \tilde{y} \right)
+\end{split}
+\end{equation}
 
-\begin{verbatim}
-\title{ This is an example of article title} }
-\author{
-   \large 1st Author \\[-3pt]
-   \normalsize 1st author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	1st author's email address \\[-3pt]
-  \and
-   \large 2nd Author \\[-3pt]
-   \normalsize 2nd author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	2nd author's email address \\[-3pt]
-\and
-   \large 3rd Author \\[-3pt]
-   \normalsize 3rd author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	3rd author's email address \\[-3pt]
-}
-\maketitle
-\end{verbatim}
+\begin{equation}
+\label{Cholesky}
+\begin{split}
+	LL = \left( X^{\top} W X \right) \\
+	\beta = L \ \backslash \ \left( X^{\top} W y \right) \\
+	\Psi = \left( L^{-1}\right)^{\top} L^{-1}
+\end{split}
+\end{equation}
 
-\subsection{Writing Julia code}
+The remaining estimators will assume a Cholesky decomposition as part of the estimation technique.
+The QR decomposition will be used in models estimated through iterative reweighted least squares (IRLS) as the factorization may be computed once and recycled.
 
-A special environment is already defined for Julia code,
-built on top of \textit{listings} and \textit{jlcode}.
+\subsection{Within Estimator}
 
-\begin{verbatim}
-\begin{lstlisting}[language = Julia]
-using Plots
+The within estimator is an application of the Frisch-Waugh-Lovell theorem \cite{FWL, FWLProof}.
+The estimator allows to compute the parameters estimates and information matrix for a subset of predictors without having to include the full set of categorical features.
+For example, one may include individual fixed effects in a large data set that may increase the dimension of the model matrix to several thousand making the problem unfeasible or inefficient.
+Moreover, some parameters may not be consistently estimated in certain contexts.
+For example, individual fixed effects are not consistently estimated when there is a fixed length for the panels (i.e., more observations implies more parameters).
 
-x = -3.0:0.01:3.0
-y = rand(length(x))
-plot(x, y)
-\end{lstlisting}
-\end{verbatim}
-\begin{lstlisting}[language = Julia]
-using Plots
+Consider the following model,
+\begin{equation}
+	y = X \beta + D \theta + e
+\end{equation}
+where $y$ is the response, $\beta$ the parameters of interest, $X$ the features of the parameters of interest, $D$ a high dimensional representation of categorical features as control, $\theta$ the parameters on said covariates, and $e$ the error term.
+In order to obtain the parameter estimates $\beta$ and the associated information matrix, we can estimate an alternative specification.
+\begin{equation}
+	\tilde{y} = \tilde{X} \beta + e
+\end{equation}
+where $\tilde{X}$ and $\tilde{y}$ are obtained by using projections, such as the annihilator matrix (i.e., $I - X \left(X^{\top}W X\right)^{-1} X^{\top})$.
+There are several methods to obtain a suitable alternative regression and these are not unique.
+\cite{reghdfe} presents several approaches to solving these problem including specialized methods in certain applications.
+Some implementations include \textit{reghdfe}, Stata module, and Matthieu Gomez \textit{FixedEffectModels.jl} package.
+The two most common approaches are solving for the residuals through a sparse least-squares problems such as with LSMR \cite{LSMR} or using some variant for the method of alternating projections.
+The residuals approach tends to be more efficient, but degrades certain aspects of the model (e.g., no longer able to obtain the mean response).
+The method of alternating projections is able to preserve under certain conditions artifacts of the original regression such as obtaining the same estimate for the intercept even though it is not particularly meaningful.
 
-x = -3.0:0.01:3.0
-y = rand(length(x))
-plot(x, y)
-\end{lstlisting}
+\subsection{Between Estimator}
 
-\subsection{Abstracts, Key words, term etc...}
-\label{subsub:abs_key_etc}
+The between estimator estimates
+\begin{equation}
+	\tilde{y} = \tilde{X} \beta + e
+\end{equation}
 
-At the beginning of your article, the title should be generated
-in the usual way using the \verb \maketitle  command. For genaral tem and keywords use
-\verb \terms ,
-\verb \keywords  commands respectively. The abstract should be enclosed
-within an abstract environment, All these environment
-can be produced using the following code:
-\begin{verbatim}
-\terms{Experimentation, Human Factors}
+where the transformed model components are collapsed through some dimension through the mean function.
+For example, one approach to obtaining the error component for a random effects model is to use model statistics of the between estimator collapsing by panel.
+The weighted version of the model uses the observation weights to compute the weighted mean values and may use the weight fractions by the collapsing dimension as weights for the weighted least squares regression on the transformed model.
 
-\keywords{Face animation, image-based modelling...}
+\subsection{Random Effects Model}
 
-\begin{abstract}
-In this paper, we propose a new method for the
-systematic determination of the model's base of
-time varying delay system. This method based on
-the construction of the classification data related
-to the considered system. The number, the orders,
-the time delay and the parameters of the local
-models are generated automatically without any
-knowledge about the full operating range of the
-process. The parametric identification of the local
-models is realized by a new recursive algorithm for
-on line identification of systems with unknown time
-delay. The proposed algorithm allows simultaneous
-estimation of time delay and parameters of
-discrete-time systems. The effectiveness of
-the new method has been illustrated through
-simulation.
-\end{abstract}
+The random effects model relies in estimating the unobserved error components.
+Random effects requires a particular schema for the data which has a panel component and a temporal component.
+There are multiple approaches, but the most common one is the Swamy-Arora approach \cite{SwamyArora}.
+This estimator uses the mean squared residuals estimates (i.e., deviance divided by residual degrees of freedom) of the between and within models using the panel dimension as the collapsing / dimension to absorb.
+The error components are estimated as
+\begin{equation}
+\begin{split}
+	\theta_{g} = 1 - \sqrt{\frac{\sigma_{e}^{2}}{T_{g} * \sigma_{u}^{2} + \sigma_{e}^{2}}} \\
+	\sigma_{e}^{2} = W \\
+	\sigma_{u}^{2} = \max\left\{0, B - \sigma_{e}^{2} * \bar{T}\right\} \\
+\end{split}
+\end{equation}
 
-\end{verbatim}
+where $W$ is the mean squared residuals of the within model, $B$ the mean squared residuals of the between model, and $T_{g}$ is the length of the panel $g$, and $\bar{T}$ is the harmonic mean of the panel lengths.
 
-\section{Some guidelines}
-\label{sec:some_guide}
-The following notes may help you achieve the best effects with the
-\verb juliacon  class file.
+The model terms are then transformed by partial demeaning
+\begin{equation}
+\begin{split}
+\tilde{y}_{it} = y_{it} - \theta_{g} * \bar{y}_{.t} \\
+\tilde{X}_{it} = X_{it} - \theta_{g} * \bar{X}_{.t}
+\end{split}
+\end{equation}
 
-\subsection{Sections}
-\label{subsub:sections}
-\LaTeXe{}  provides four levels of section headings and they are all
-defined in the \verb juliacon  class file:
-\begin{itemize}
-\item \verb \section   \item \verb \subsection  \item \verb \subsubsection  \item \verb \paragraph  \end{itemize}
-Section headings are automatically converted to allcaps style.
-\subsection{Lists}
-\label{sec:lists}
-%
-The \verb juliacon   class file provides unnumbered lists using the
-\verb unnumlist  environment for example,
+and these are used in the standard regression setting.
 
-\begin{unnumlist}
-\item First unnumbered item which has no label and is indented from the
-left margin.
-\item Second unnumbered item.
-\item Third unnumbered item.
-\end{unnumlist}
-The unnumbered list which has no label and is indented from the
-left margin. was produced by:
-\begin{verbatim}
-\begin{unnumlist}
-\item First unnumbered item...
-\item Second unnumbered item...
-\item Third unnumbered item...
-\end{unnumlist}
-\end{verbatim}
+\subsection{First-Difference}
 
-The \verb juliacon   class file also provides hyphen list using the
-\verb itemize  environment for example,
-\begin{itemize}
-\item First unnumbered bulleted item which has no label and is indented
-from the left margin.
-\item Second unnumbered bulleted item.
-\item Third unnumbered bulleted item which has no label and is indented
-from the left margin.
-\end{itemize}
-was produced by:
-\begin{verbatim}
-\begin{itemize}
-\item First item...
-\item Second item...
-\item Third item...
-\end{itemize}
-\end{verbatim}
+The first-difference estimator is a special case that use time / panel context for feature designs.
+The most common transformations include contrasts such as treatment coding (dummy coding), sum coding (effects coding) or Helmert coding which apply to categorical variables.
+Other common feature engineering techniques include log-transform and polynomial terms.
+However, certain transformations require a context such as a time dimension.
+Some examples include shift operations (lag, lead) and differentiating (e.g., first-difference).
+These operations may optionally require a group context such that the operations are performed group wise.
+Time-context operations have important concepts such as frequency and gaps.
+The frequency describes the difference between periods/observations and gaps describe observations that are skipped and should be understood as missing.
 
-Numbered list is also provided in acmtog class file using the
-enumerate environment for example,
-\begin{enumerate}
-\item The attenuated and diluted stellar radiation.
-\item Scattered radiation, and
-\item Reradiation from other grains.
-\end{enumerate}
+\subsection{Instrumental Variables}
 
-was produced by:
-\begin{verbatim}
-\begin{enumerate}
-\item The attenuated...
-\item Scattered radiation, and...
-\item Reradiation from other grains...
-\end{enumerate}
-\end{verbatim}
-\subsection{Illustrations (or figures)}
-\label{subsub:sec_Illus}
-The \verb juliacon   class file will cope with most of the positioning of
-your illustrations and you should not normally use the optional positional
-qualifiers on the \verb figure   environment that would override
-these decisions.
-\vskip 6pt
+Every estimator thus far can be generalized to include endogenous covariates through instrumental variables.
+The most common method is through two stages least squares (2SLS).
+The idea is to first apply all the relevant transformations to the model terms and apply the 2SLS standard procedure.
+In the case of the random effects model, the within and between models are estimated using 2SLS to obtain the error component estimates.
+After applying the random effects transformation to each model term the 2SLS process is employed in the final regression model à la \cite{BV_1987}.
 
-%
-\begin{figure}[t]
-\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
-\caption{This is example of the image in a column.}
-	\label{fig:sample_figure}
+The standard 2SLS estimator uses,
+\begin{equation}
+\begin{split}
+\hat{z} = [X Z] \left[ \left( [X Z]^{\top} W [X Z] \right)^{-1} [X Z]^{\top} W z\ \right] \\
+\hat{\beta} = \left( [X \hat{z}]^{\top} W [X \hat{z}] \right)^{-1} [X \hat{z}]^{\top} W y \\
+\Psi = \left( [X \hat{z}]^{\top} W [X \hat{z}] \right)^{-1} \\
+\hat{y} = [X z] \hat{\beta}
+\end{split}
+\end{equation}
+
+for each model where $z$ is endogenous variables and $Z$ the additional instruments.
+
+\subsection{Nominal Response Model}
+
+Multinomial logistic regression is a probability model for estimating probabilities across multiple categories.
+It is a vector generalized linear model with softmax link function and the categorical distribution.
+It is estimated through iterative re-weighted least squares (IRLS) methods such as the QR Newton variant \cite{OLeary_1990}.
+The data schema for discrete choice models include the response (observed behavior), unit of observation covariates, and outcomes-specific covariates.
+The initial implementation allows for the base case of no-outcome specific features.
+
+\subsection{Ordinal Response Model}
+
+Ordinal logistic regression is a probability model for estimating probabilities across multiple ordered categories.
+Similarly to its nominal counterpart, it has a pool of alternatives, and observed outcome, unit of observation covariates, and outcome-specific covariates.
+A common assumption is the proportional odds assumption which may be relaxed in other models.
+
+The log-likelihood function has the same form as the general form for computing the cost associated with a categorical distribution and predicted probability for realization. More specific,
+\begin{equation}
+	\ell \ell = \sum_{i = 1}^{m} \sum_{k}^{K} \mathbbm{1}\left(y_{i} = k\right) \ln\left[F\left(\alpha_{k + 1} - \eta\right) - F\left(\alpha_{k} - \eta\right)\right]
+\end{equation}
+
+where $F$ is the cumulative distribution function of the logistic distribution with zero location and unit scale, $\eta$ is the linear projection, and $\alpha_{k}$ is the threshold for lower threshold \cite{ologit}.
+The log-likelihood function and the gradient are passed to the \textit{Optim.jl} framework \cite{Optim} using \textit{ForwardDiff.jl} \cite{ForwardDiff} forward mode automatic differentiation (AD) for the Newtonian solver.
+
+\subsection{Count/Rate Model}
+
+Count/rate models are generalized linear models and follow a similar description as nominal models.
+The most common distribution choices are Poisson and Negative Binomial with the log link function.
+Negative Binomial is a generalization of the Poisson model, which adds an extra parameter for modeling the second moment (i.e., relaxes the mean equal variance assumption in the Poisson model).
+For the Negative Binomial to be a distribution in the exponential family it needs a restriction parameter which may be optimized through maximum likelihood estimation.
+An offset may be included to handle rates, a generalization of counts, that account for differences in exposures.
+Other generalizations include additive or multiplicative errors relations.
+
+\subsection{Duration Models}
+
+Duration models deal with responses of the type time until an event.
+One such model is the Cox proportional hazards model which relies on the proportional hazards assumption.
+Various models of these kind may be re-specified in a generalized linear model framework relating to the previous descriptions.
+
+\section{Technical Challenges}
+
+One technical challenge that is prevalent through every model is the issue of rank deficient terms.
+Rank deficient systems of linear equations are not identifiable.
+One approach is to error out and let the user explore and find a subset of features such that the no multi-collinearity assumption holds.
+The second approach is to automatically promote the system to a full rank version by excluding linearly dependent features.
+How much collinearity is too much is not an exact science.
+Some potential criteria include using the absolute values of the diagonal in the triangular matrix of the factorization (e.g., $L$ in $LL^{\top}$, $R$ in $QR$, $D$ in $LDL^{\top}$, $\Sigma$ in $U\Sigma V^{\top}$).
+These values are then compared against a chosen tolerance and the column of the term is deemed linearly independent if the values are greater than the tolerance.
+Note that Cholesky, QR, and Bunch-Kaufman decomposition allow to identify which columns are independent while singular values only allow to determine the rank.
+It may be arbitrary to choose among linearly dependent features.
+An additional level of complexity in probability models is the issue of linearly separability.
+\cite{Konis_2007} provides an overview of potential approaches to identifying the issue.
+
+\section{Julia Ecosystem}
+
+The usual pipeline for regression analysis involves (1) accessing data (I/O), (2) obtaining a tabular data representation, (3) data wrangling, and (4) employing regression analysis tools.
+The Julia ecosystem follows this canonical pipeline.
+The following sections provides an overview of the pipeline available in Julia.
+
+\subsection{Data to Modeling}
+
+\textit{StatsBase.jl} builds on top of Statistics.jl (standard library) to provide additional statistical functionality.
+One which includes the abstraction for Statistical Models (and Regression models which inherit from the former).
+It provides a simple and powerful API for the whole Julia ecosystem to use.
+It allows packages to implement the API and easily support a common functionality users can expect and interact with in a familiar manner.
+For example, \textit{coef} will extract the parameter estimates from any object that implements the API.
+The full API include model statistics such as: coefficient of determination (or adjusted), information criteria statistics such as AIC/BIC (and corrected), statistics about the model fitness such as deviance, log-likelihood, and usual queries such as point estimates, variance covariance estimates, standard errors, confidence intervals, degrees of freedom (or residual degrees of freedom), etc.
+Lastly, several accessors are available for fitted values, response, model matrix, information matrix, leverage values, error components, etc.
+Lastly, it also provides an abstraction for weights including frequency weights and analytical weights.
+
+\textit{Tables.jl} provide an interface for tabular data.
+This API allows users to choose from various solutions the tabular data implementation of their choosing without having to worry that their choice will limit potential functionality.
+Many tabular implementations such as \textit{DataFrames.jl} provide robust functionality to many routines such as handling categorical features, dates/time, missing values, reshaping data, split/apply operations, and others.
+Users need not to worry about any I/O issues as a rich array of options exist for importing and exporting across different file formats such as delimiter-separated values, JSON, Feather, HDF5, MATLAB, Stata, SPSS, SAS, and R.
+
+\textit{StatsModels.jl} is a package that provides the means to go from data to model terms.
+It provides the formulae language (e.g., similar syntax to R's formulae syntax).
+A model is then build using a formula, data, and additional model specific arguments.
+The process can be summarized as (1) collecting the information in the formula, (2) parsing its meaning by applying a schema based on the data, user-specified contrasts or other arguments, and (3) generating the model terms such as a response, model matrices, etc.
+Lastly, a package fits said model and implements the API.
+
+\subsection{Regression Analysis}
+
+The regression analysis ecosystem in Julia has \textit{GLM.jl} as its flagship.
+\textit{GLM.jl} provides the typical functionality for fitting generalized linear models through Fisher scoring.
+This includes linear models, Poisson/Negative Binomial, Logit/Probit, and other non-canonical link models.
+\textit{CovarianceMatrices.jl} provides various variance covariance estimators for \textit{GLM.jl} models à la R's \textit{sandwich} package.
+\textit{LinearMixedModels.jl} \cite{LinearMixedModels} extends \textit{GLM.jl} for mixed-effects models.
+\textit{FixedEffectModels.jl} provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la \textit{reghdfe}.
+\textit{Survival.jl} provides a series of estimators for duration models.
+Two major gaps in the ecosystem include estimating nominal and ordinal response models (i.e., discrete choice) with more than two alternatives and support for longitudinal estimators.
+
+\section{Econometrics.jl}
+
+\textit{Econometrics.jl} is a package for performing several common econometrics routines in the Julia language.
+It aims to provide the following functionality for two major gaps in the ecosystem, longitudinal estimators and discrete choice models.
+Developing the package has resulted in many contributions in the current ecosystem.
+However, the development of this package serves multiple purposes beyond the immediate effect.
+As the statistics ecosystem evolves and matures, \textit{Econometrics.jl} aims to serve as inspiration and an alternative to design decisions, standards, and option for user.
+
+\subsection{Fitting Models}
+
+This section will showcase some examples of using the package for various estimators.
+For each estimator a brief description of the data, model, syntax, and output will be provided.
+Results will be provided for Econometrics.jl and some alternatives such as R or Stata.
+
+For linear models, the examples use the crime data set from \cite{Crime}.
+The data set is a balanced longitudinal data set with 90 counties in North Carolina from 1981 to 1987.
+The outcome variable is the crime rate and the explanatory variables include the probability of conviction, average sentence, and probability of prison sentence.
+Estimating the pooling estimator or between estimators can be accomplished as in figure \vref{estimator_pooling} and \vref{estimator_between}.
+Table \vref{poberes} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.
+
+\begin{figure}[hbpt]
+    \includegraphics[max width=\linewidth,center]{estimator_pooling}
+	\caption{Estimation of the pooling estimator}
+	\label{estimator_pooling}
 \end{figure}
 
-The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
-organization \footnote{https://github.com/JuliaGraphs}.
+\begin{figure}[hbpt]
+    \includegraphics[max width=\linewidth,center]{estimator_between}
+	\caption{Estimation of the between panel estimator}
+	\label{estimator_between}
+\end{figure}
 
-Figure captions should be \emph{below} the figure itself, therefore the
-\verb \caption  command should appear after the figure or space left for
-an illustration. For example, Figure 1 is produced using the following
-commands:
+The fixed effects model or within estimator can be estimated as in figure \vref{withinmodel} which estimates the panel effects and the two-ways fixed effects model (i.e., fixed effects for time dimension as well).
+Table \vref{withinres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.
 
-\begin{verbatim}
-\begin{figure}
-\centerline{\includegraphics[width=20pc]{Graphics.eps}}
-\caption{An example of the testing process for a
-binary tree. The globa null hypothesis is tested
-first at level $\alpha$ (a), and the level of
-individual variables is reached last (d). Note
-that individual hypotheses can be tested at
-level $\alpha/4$ and not $\alpha/8$ as one might
-expect at first.}
-\label{sample-figure_2}
+\begin{figure}[hbpt]
+	\includegraphics[max width=\linewidth,center]{estimator_within}
+	\caption{Estimation of the within estimator}
+	\label{withinmodel}
 \end{figure}
-\end{verbatim}
-Figures can be resized using first and second argument of
-\verb \includegraphics   command. First argument is used for modifying
-figure height and the second argument is used for modifying
-figure width respectively.
-\vskip 6pt
-Cross-referencing of figures, tables, and numbered, displayed
-equations using the \verb \label  and \verb \ref   commands is encouraged.
-For example, in referencing Figure 1 above, we used
-\verb Figure~\ref{sample-figure}   \subsection{Tables}
-\label{subsub:sec_Tab}
-The \verb juliacon   class file will cope with most of the positioning of
-your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
-decisions. Table captions should be at the top.
-\begin{verbatim}
-\begin{table}
-\tbl{Tuning Set and Testing Set}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Train70 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test70 & Testing Data I & & 105\\\hline
-Test30 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\end{table}\end{verbatim}
 
-\begin{table}
-\tbl{Tuning Set and Testing Set}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Test 1 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test 2 & Testing Data I & & 105\\\hline
-Test 3 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\end{table}
-\subsection{Landscaping Pages}
-\label{subsub:landscaping_pages}
-If a table is too wide to fit the standard measure, it may be turned,
-with its caption, to 90 degrees. Landscape tables cannot be produced
-directly using the \verb juliacon   class file because \TeX{} itself cannot
-turn the page, and not all device drivers provide such a facility.
-The following procedure can be used to produce such pages.
-\vskip 6pt
-Use the package \verb rotating   in your document and change the coding
-from
-\begin{verbatim}
-\begin{table}...\end{table}
-to
-\begin{sidewaystable}...\end{sidewaystable}
-and for figures
-\begin{figure}...\end{figure}
-to
-\begin{sidewaysfigure}...\end{sidewaysfigure}
-\end{verbatim}
+\begin{figure}[hbpt]
+	\includegraphics[max width=\linewidth,center]{estimator_within2}
+	\caption{Estimation of the within estimator with multiple fixed effects}
+	\label{within2model}
+\end{figure}
 
-environments in your document to turn your table on the appropriate
-page of your document. For instance, the following code prints
-a page with the running head, a message half way down and the
-table number towards the bottom.
-\begin{verbatim}
-\begin{sidewaystable}
-\tbl{Landscape table caption to go here.}{...}
-\label{landtab}
-\end{sidewaystable}
-\end{verbatim}
+The random effects model can be estimated with similar syntax by including the \textit{PID} (panel identifier) and \textit{TID} (temporal identifier) tags such as in figure \vref{random} which shows estimating a random effects model as well as its instrumental variables counterpart.
+Table \vref{xtregres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata's reghdfe module, and R's plm package.
 
-\subsection{Double Column Figure and Tables}
-\label{subsub:double_fig_tab}
-For generating the output of figures and tables in double column
-we can use the following coding:
+\begin{figure}[hbpt]
+	\includegraphics[max width=\linewidth,center]{estimator_re}
+	\caption{Estimation of the random effects model}
+	\label{random}
+\end{figure}
 
-\begin{enumerate}
-\item For Figures:
-\begin{verbatim}
-\begin{figure*}...\end{figure*}
-\end{verbatim}
-\item For landscape figures:
-\begin{verbatim}
-\begin{sidewaysfigure*}...\end{sidewaysfigure*}
-\end{verbatim}
-\item For Tables:
-\begin{verbatim}
-\begin{table*}...\end{table*}
-\end{verbatim}
-\item For landscape tables:
-\begin{verbatim}
-\begin{sidewaystable*}...\end{sidewaystable*}
-\end{verbatim}
-\end{enumerate}
+The sysdsn1 Stata example health insurance data set is used to illustrate the multinominal logistic regression when the response is nominal as seen in figure \vref{mlogit}.
+A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl and Stata is shown in table \vref{mlogitres}.
 
-\subsection{Typesetting Mathematics}
-\label{subsub:type_math}
-The \verb juliacon class file will set displayed mathematics with center to
-the column width, provided that you use the \LaTeXe{} standard of
-open and closed square brackets as delimiters.
-The equation
-\[
-\sum_{i=1}^p \lambda_i = (S)
-\]
+\begin{figure}[hbpt]
+	\includegraphics[max width=\linewidth,center]{estimator_mlogit}
+	\caption{Estimation of the multinomial logistic regression}
+	\label{mlogit}
+\end{figure}
 
-was typeset using the acmtog class file with the commands
+The fullauto Stata example automobile models data set is used to illustrate the proportional ordinal logistic regression when the response is ordinal as seen in figure \vref{ologit}.
+A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl, Stata, and R's MASS is shown in table \vref{ologitres}.
 
-\begin{verbatim}
-\[
-\sum_{i=1}^p \lambda_i = (S)
-\]
-\end{verbatim}
+\begin{figure}[hbpt]
+	\includegraphics[max width=\linewidth,center]{estimator_ologit}
+	\caption{Estimation of the proportional odds logistic regression}
+	\label{ologit}
+\end{figure}
 
-For display equations, cross-referencing is encouraged. For example,
-\begin{verbatim}
-\begin{equation}
-(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
-\label{eq:samplevar}
-\end{equation}
-Equation~(\ref{eq:samplevar}) gives the formula for
-sample variance.
-\end{verbatim}
-The following output is generated with the above coding:
-\begin{equation}
-(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
-\label{eq:samplevar}
-\end{equation}
-Equation~(\ref{eq:samplevar}) gives the formula for
-sample variance.
+\subsection{Design Decisions}
 
-\subsection{Enunciations}
-\label{subsub:enunciation}
-The \verb juliacon   class file generates the enunciations with the help of
-the following commands:
-\begin{verbatim}
-\begin{theorem}...\end{theorem}
-\begin{strategy}...\end{strategy}
-\begin{property}...\end{property}
-\begin{proposition}...\end{proposition}
-\begin{lemma}...\end{lemma}
-\begin{example}...\end{example}
-\begin{proof}...\end{proof}
-\begin{definition}...\end{definition}
-\begin{algorithm}...\end{algorithm}
-\begin{remark}...\end{remark}
-\end{verbatim}
-The above-mentioned coding can also include optional arguments
-such as
-\begin{verbatim}
-\begin{theorem}[...]. Example for theorem:
-\begin{theorem}[Generalized Poincare Conjecture]
-Four score and seven ... created equal.
-\end{theorem}
-\end{verbatim}
+Statistical software developers play a very powerful role in shaping culture and norms.
+For example, whether to default to maximum likelihood estimation (MLE) or restricted maximum likelihood estimation (REML), can shape not only choices by practitioners, but by stakeholders, regulatory agencies, and expected components for reports.
+These changes may be good or bad depending on the case.
+For example, advances in econometrics are rarely widely adopted without buy-in from software developers.
+The following discussions will survey survey some of the decisions relevant to \textit{Econometrics.jl}.
 
-\begin{theorem}[Generalized Poincare Conjecture]
-Four score and seven years ago our fathers brought forth,
-upon this continent, a new nation, conceived in Liberty,
- and dedicated to the proposition that all men are
-created equal.
-\end{theorem}
+Should software be dummy-proof?
+Many times software developers have to choose between exposing users to make mistakes on their own volition or put safeguard against potential misuses by restricting behavior that may be correct under rare scenarios.
+For example, a basic tool might allow users to mix and match link and distributions in a GLM settings even if the combinations are nonsensical.
+A safer approach would be to restrict combinations to those ``safe'' combinations such as distributions with canonical links.
+The trade-off occurs when users may encounter a specification that while uncommon it may be the correct one for that particular model.
+Currently, \textit{Econometrics.jl} takes a conservative approach that provides ``dummy-proof'' experience as well as ease of use.
+For example, rather than requiring users to specify the model, the estimator is inferred based on the type of the response and information provided.
+Other examples of this approach include making model statistics such as promoting the coefficient of determination to a pseudo-version for non-linear models (a generalization of the linear case), but providing a \textit{not a number} (NaN) value for instrumental variable models or those that do not include an intercept.
+Similarly, the software will promote terms to full rank as required and inform of the behavior.
 
-\subsection{Extract}
-\label{subsub:extract}
-Extract environment should be coded within
-\begin{verbatim}
-\begin{extract}..\end{extract}
-\end{verbatim}
+Software analysis should always include diagnostics and tools to make it easier for dissemination.
+Many tests and diagnostics are applicable to a wide set of implementations.
+The best manner to make these available and for these to ``play nicely'' with one another is to have an effective API.
+Sadly, the Julia ecosystem has yet to experience wide adoption of this pattern.
+For example, packages might need to access components for computing a test or providing some estimates such as variance covariance estimates.
+The test might include components such as the residual degrees of freedom, the information matrix, residuals, and score.
+Many implementations might access internals of one particular implementation and compute these such as obtaining the model matrix, response and coefficients to compute the residuals.
+This behavior would produce incorrect estimates in cases of instrumental variable as the fitted / linear projection should not use the model matrix, but replace the projection of endogenous features with their actual values.
+A better approach would be to request the response and fitted values to compute the residuals.
+This approach is less prone to errors, but it can be more robust by calling residuals directly.
+Specifying precise components can alleviate risk of errors or relying on assumptions such as whether the components are weighted or should be weighted for the procedure.
 
-\subsection{Balancing column at last page}
-\label{subsub:Balance}
-For balancing the both column length at last page use :
-\begin{verbatim}
-\vadjust{\vfill\pagebreak}
-\end{verbatim}
+Various decisions are software specific with asymptotic justification, but significant finite-sample consequences.
+Software may differ on whether to report statistics using finite-sample statistics (t-distribution, F-distribution) or asymptotic equivalent counterparts (Normal, Chi squared).
+These tend to have negligible effect in most applications, but other decisions such as degrees of freedom may have larger consequences.
+For example, software may differs on how it computes the degrees of freedom for instrumental variables or absorbed variables depending on the context (e.g., main regression or auxiliary regression for estimating error components).
+Refinements and robustness checks can also contribute to a better analysis such as verifying gaps for time variant operations such as first-difference or purging singletons and other degree of freedom adjustments à la \cite{Singletons}.
 
-%\vadjust{\vfill\pagebreak}
+\subsection{Best Practices}
 
-at appropriate place in your \TeX{} file or in bibliography file.
+\textit{Econometrics.jl} adopts the best practices standards for open-source statistical software.
+These include adhering to semantic versioning (semver) for descriptive versioning, continuous integration for development, software validation through a comprehensive code coverage and test suite, and lastly online hosted documentation for the public API.
 
-\section{Handling references}
-\label{subsub:references}
-References are most easily (and correctly) generated using the
-BIBTEX, which is easily invoked via
-\begin{verbatim}
-\bibliographystyle{juliacon}
-\bibliography{ref}
-\end{verbatim}
-When submitting the document source (.tex) file to external
-parties, the ref.bib file should be sent with it.
-\cite{bezanson2017julia}
+\section{Conclusion}
+
+\textit{Econometrics.jl} is a new addition to the Julia ecosystem that brings highly demanded functionality concerning longitudinal estimators and discrete choice models.
+This study serves as a complement to the software documentation providing context to the development, design considerations, and roadmap of the project.
+A philosophical motivation for the project is to make econometrics accessible to practitioners not only through functionality, but transparency in the code readability, replicability, and correctness.
+For example, transparent well-written code is easier to maintain, inspect / audit, and can be useful for learning and teaching.
+
+Community contributions and feedback are highly encouraged in order to best continue developing the project.
+The release will be available at the Github repository and licensed under a permissive license.
+
+\vfill
 
 \input{bib.tex}
+
+\appendix
+\onecolumn
+\input{figures/pobe.tex}
+\input{figures/fem.tex}
+\input{figures/xtreg.tex}
+\input{figures/mlogit.tex}
+\input{figures/polr.tex}
 

### 2019-06-26 src/Econometrics.jl
StatsModels 0.6 tagged
Updated code to rely on tagged StatsModels

@@ -5,30 +5,33 @@
 """
 module Econometrics
     using Base.Iterators: flatten
-    using LinearAlgebra: bunchkaufman, bunchkaufman!, cholesky!, diag, diagm, Diagonal,
-                         Hermitian, I, LowerTriangular, qr, UpperTriangular
-    using DataFrames: AbstractDataFrame, categorical!, DataFrame, dropmissing,
-                      # CategoricalArrays
-                      AbstractCategoricalVector, categorical, levels, isordered
     using Distributions: cdf, ccdf, Categorical, Chisq, FDist, logpdf, Logistic, Normal,
                          pdf, TDist,
                          # Statistics
                          mean, quantile, var,
                          # StatsFuns
-                         softmax
+                         softmax,
+                         # LinearAlgebra
+                         bunchkaufman, bunchkaufman!, cholesky!, diag, diagm, Diagonal,
+                         Hermitian, I, LowerTriangular, qr, UpperTriangular,
+                         # Printf
+                         @sprintf
     using FillArrays: Ones
     using Optim: hessian!, optimize, minimizer, TwiceDifferentiable,
                  # ForwardDiff
                  ForwardDiff.Dual, ForwardDiff.value
     using Parameters: @unpack
-    using Printf: @sprintf
     using StatsModels: AbstractContrasts, AbstractTerm, apply_schema, CategoricalTerm,
                        ConstantTerm, ContrastsMatrix, DummyCoding, @formula, FormulaTerm,
                        FunctionTerm, InterceptTerm, MatrixTerm, modelcols, schema, terms,
                        termvars,
                        # StatsBase
                        aic, aicc, bic, harmmean, FrequencyWeights, CoefTable,
-                       ConvergenceException
+                       ConvergenceException,
+                       # CategoricalArrays
+                       AbstractCategoricalVector, categorical, levels, isordered,
+                       # Missings
+                       disallowmissing
     import Base: show
     import StatsModels: hasintercept, implicit_intercept,
                         # StatsBase
@@ -42,7 +45,7 @@ module Econometrics
     foreach(file -> include(joinpath(dirname(@__DIR__), "src", "$file.jl")),
             ["structs", "transformations", "formula", "solvers", "main", "statsbase", "wald"])
 
-    export categorical!, DataFrame, @formula, DummyCoding, aic, aicc, bic, coef, coefnames,
[…]

### 2019-06-26 src/formula.jl

@@ -4,8 +4,10 @@ function TID end
 function between end
 function vce end
 
-function decompose(f::FormulaTerm, data::AbstractDataFrame, contrasts::Dict{Symbol})
-    data = dropmissing(data[termvars(f)], disallowmissing = true)
+function decompose(f::FormulaTerm, data, contrasts::Dict{Symbol})
+    data = filter(row -> all(!ismissing, row), data[termvars(f)])
+    foreach(pn -> data[pn] = disallowmissing(data[pn]),
+            propertynames(data))
     rhs = isa(f.rhs, Tuple) ? collect(f.rhs) : [f.rhs]
     absorbed = findall(t -> isa(t, FunctionTerm{typeof(absorb)}), rhs)
     if isempty(absorbed)

### 2019-06-26 src/main.jl

@@ -1,7 +1,7 @@
 """
-    EconometricModel(f::FormulaTerm, data::AbstractDataFrame;
+    EconometricModel(f::FormulaTerm, data;
                      contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}})
-    
+
     Use fit(EconometricModel, f, data, contrasts = contrasts)
     Formula has syntax: @formula(response ~ exogenous + (endogenous ~ instruments) +
                                  weights(wts))
@@ -11,6 +11,7 @@
 """
 mutable struct EconometricModel{E<:ModelEstimator,
                                 F<:FormulaTerm,
+                                D<:Any,
                                 Y<:AbstractVecOrMat{<:Number},
                                 W<:FrequencyWeights,
                                 Ŷ<:AbstractVecOrMat{<:Float64},
@@ -19,7 +20,7 @@ mutable struct EconometricModel{E<:ModelEstimator,
                                          <:AbstractVector{<:AbstractString}}} <: EconometricsModel
     estimator::E
     f::F
-    data::DataFrame
+    data::D
     X::Matrix{Float64}
     y::Y
     w::W
@@ -109,7 +110,7 @@ function show(io::IO, obj::EconometricModel{<:OrdinalResponse})
 end
 function fit(::Type{<:EconometricModel},
              f::FormulaTerm,
-             data::AbstractDataFrame;
+             data;
              contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}}())
     data, f, exogenous, iv, absorbed, pid, tid, wts, effect, y, X, z, Z =
         decompose(deepcopy(f), data, contrasts)

### 2019-06-26 dev/search_index.js
build based on 446ac4e

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"#Econometrics-1","page":"Econometrics","title":"Econometrics","text":"","category":"section"},{"location":"#Setup-1","page":"Econometrics","title":"Setup","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"using Econometrics, CSV, RDatasets","category":"page"},{"location":"#Continuous-Response-Models-1","page":"Econometrics","title":"Continuous Response Models","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"data = RDatasets.dataset(\"Ecdat\", \"Crime\") |>\n  (data -> select(data, [:County, :Year, :CRMRTE, :PrbConv, :AvgSen, :PrbPris]))\nfirst(data, 6)","category":"page"},{"location":"#Pooling-1","page":"Econometrics","title":"Pooling","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris),\n            data)","category":"page"},{"location":"#Between-1","page":"Econometrics","title":"Between","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + between(County)),\n            data)","category":"page"},{"location":"#Within-1","page":"Econometrics","title":"Within","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(County)),\n            data)","category":"page"},{"location":"#Within-(two-ways)-1","page":"Econometrics","title":"Within (two-ways)","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(County + Year)),\n            data)","category":"page"},{"location":"#Random-1","page":"Econometrics","title":"Random","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE 
[…]

### 2019-06-27 src/Econometrics.jl
Fixed bug with ContinousModel dof

@@ -27,11 +27,14 @@ module Econometrics
                        termvars,
                        # StatsBase
                        aic, aicc, bic, harmmean, FrequencyWeights, CoefTable,
-                       ConvergenceException,
+                       ConvergenceException, Weights,
                        # CategoricalArrays
                        AbstractCategoricalVector, categorical, levels, isordered,
                        # Missings
-                       disallowmissing
+                       disallowmissing,
+                       # Tables
+                       Tables.columns, Tables.columntable, Tables.select, Tables.rows,
+                       Tables.materializer
     import Base: show
     import StatsModels: hasintercept, implicit_intercept,
                         # StatsBase

### 2019-06-27 src/formula.jl

@@ -5,7 +5,18 @@ function between end
 function vce end
 
 function decompose(f::FormulaTerm, data, contrasts::Dict{Symbol})
-    data = filter(row -> all(!ismissing, row), data[termvars(f)])
+    pns = termvars(f)
+    # data = data |>
+    # columntable |>
+    # (table -> select(table, pns...)) |>
+    # (table -> filter!(row -> all(!ismissing(getproperty(row, pn)) for pn ∈ pns),
+    #                   collect(rows(table)))) |>
+    # (table -> materializer(table)(table)) |>
+    # (table -> map(disallowmissing, columns(table)))
+    # (table -> materializer(table)(table))
+    data = data[pns]
+    data = data[map(row -> all(!ismissing(getproperty(row, pn)) for pn ∈ pns),
+                rows(data)),:]
     foreach(pn -> data[pn] = disallowmissing(data[pn]),
             propertynames(data))
     rhs = isa(f.rhs, Tuple) ? collect(f.rhs) : [f.rhs]

### 2019-06-27 src/main.jl

@@ -32,9 +32,9 @@ mutable struct EconometricModel{E<:ModelEstimator,
 end
 function show(io::IO, obj::EconometricModel{<:LinearModelEstimators})
     show(io, obj.estimator)
-    ℓℓ = loglikelihood(obj)
     println(io, @sprintf("Number of observations: %i", nobs(obj)))
-    println(io, @sprintf("Loglikelihood: %.2f", ℓℓ))
+    println(io, @sprintf("Null Loglikelihood: %.2f", nullloglikelihood(obj)))
+    println(io, @sprintf("Loglikelihood: %.2f", loglikelihood(obj)))
     println(io, @sprintf("R-squared: %.4f", r2(obj)))
     W, F, p = wald(obj)
     if !isnan(p)
@@ -49,7 +49,7 @@ function show(io::IO, obj::EconometricModel{<:ContinuousResponse})
     ℓℓ = loglikelihood(obj)
     absorbed = !isempty(obj.estimator.groups)
     println(io, @sprintf("Number of observations: %i", nobs(obj)))
-    absorbed || println(io, @sprintf("Null Loglikelihood: %.2f", ℓℓ₀))
+    println(io, @sprintf("Null Loglikelihood: %.2f", ℓℓ₀))
     println(io, @sprintf("Loglikelihood: %.2f", ℓℓ))
     println(io, @sprintf("R-squared: %.4f", r2(obj)))
     if !absorbed

### 2019-06-27 src/solvers.jl

@@ -4,11 +4,16 @@
                       z::AbstractVecOrMat{<:Number},
                       Z::AbstractMatrix{<:Number},
                       wts::AbstractVector)
+    if !isa(wts, Weights)
+        wts = FrequencyWeights(wts)
+    else
+        isa(wts, FrequencyWeights) || throw(ArgumentError("Only frequency weights are supported."))
+    end
     X = transform(estimator, X, wts)
     y = transform(estimator, y, wts)
     z = transform(estimator, z, wts)
     Z = transform(estimator, Z, wts)
-    w = transform(estimator, wts)
+    w = transform(estimator, FrequencyWeights(wts))
     if !isempty(z)
         Z̃ = hcat(X, Z)
         F = bunchkaufman!(Hermitian(Z̃' * Diagonal(w) * Z̃), true)
@@ -22,6 +27,39 @@
     Ψ = Hermitian(inv(F))
     ŷ = isempty(z) ? X * β : hcat(X, z) * β
     X, y, β, Ψ, ŷ, w, collect(1:size(X̃, 2))
+end
+@views function solve(estimator::ContinuousResponse,
+                      X::AbstractMatrix{<:Number},
+                      y::AbstractVector{<:Number},
+                      z::AbstractVecOrMat{<:Number},
+                      Z::AbstractMatrix{<:Number},
+                      wts::AbstractVector)
+    if !isa(wts, Weights)
+        wts = FrequencyWeights(wts)
+    else
+        isa(wts, FrequencyWeights) || throw(ArgumentError("Only frequency weights are supported."))
+    end
+    y₀ = y
+    X = transform(estimator, X, wts)
+    y = transform(estimator, y, wts)
+    z = transform(estimator, z, wts)
+    Z = transform(estimator, Z, wts)
+    w = transform(estimator, FrequencyWeights(wts))
+    if !isempty(z)
+        Z̃ = hcat(X, Z)
+        F = bunchkaufman!(Hermitian(Z̃' * Diagonal(w) * Z̃), true)
+        γ = F \ (Z̃' * Diagonal(w) * z)
+        X̃ = hcat(X, Z̃ * γ)
+    else
+        X̃ = X
+    end
[…]

### 2019-06-27 src/statsbase.jl

@@ -30,7 +30,7 @@ function loglikelihood(obj::EconometricModel{<:Union{NominalResponse,OrdinalResp
 	sum(wts[idx[1]] * logpdf(Categorical(collect(μ[idx[1],:])), idx[2]) for idx in findall(b))
 end
 function nullloglikelihood(obj::EconometricModel{<:LinearModelEstimators})
-	ϕ = √(nulldeviance(obj) / (dof_residual(obj) + (length(coef(obj)) - hasintercept(obj))))
+	ϕ = √(nulldeviance(obj) / (dof_residual(obj) + (dof(obj) - hasintercept(obj))))
 	μ = meanresponse(obj)
 	sum(w * logpdf(Normal(μ, ϕ), y) for (w, y) ∈ zip(weights(obj), response(obj)))
 end

### 2019-06-27 test/runtests.jl

@@ -1,4 +1,6 @@
-using Test, Econometrics, CSV, RDatasets, LinearAlgebra
+using Test, Econometrics, RDatasets
+using Econometrics: Hermitian
+using RDatasets: CSV
 
 # Linear Models
 @testset "Linear Models" begin
@@ -30,7 +32,7 @@ using Test, Econometrics, CSV, RDatasets, LinearAlgebra
     model = fit(EconometricModel,
                 @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + between(County)),
                 data)
-	@test sprint(show, model) == "Between Estimator\nCounty with 630 groups\nBalanced groups with size 7\nNumber of observations: 90\nLoglikelihood: 244.40\nR-squared: 0.1029\nWald: 3.29 ∼ F(3, 86) ⟹  Pr > F = 0.0246\nFormula: CRMRTE ~ PrbConv + AvgSen + PrbPris + :(between(County))\n───────────────────────────────────────────────────────────────────────────────────\n                    PE          SE       t-value  Pr > |t|         2.5%       97.5%\n───────────────────────────────────────────────────────────────────────────────────\n(Intercept)  -0.00464339   0.0186571   -0.24888     0.8040  -0.0417325   0.0324457 \nPrbConv      -0.00354113   0.0018904   -1.87322     0.0644  -0.00729911  0.00021685\nAvgSen        0.000848049  0.00116477   0.728086    0.4685  -0.00146743  0.00316353\nPrbPris       0.0730299    0.0332057    2.19932     0.0305   0.0070191   0.139041  \n───────────────────────────────────────────────────────────────────────────────────"
[…]

### 2019-07-03 src/formula.jl
Rank-deficient models

@@ -7,9 +7,6 @@ function decompose(f::FormulaTerm,
                    panel::Union{Nothing,Symbol},
                    time::Union{Nothing,Symbol},
                    estimator::Type{<:Union{EconometricsModel,ModelEstimator}})
-    # panel = nothing
-    # time = nothing
-    # wts = nothing
     rhs = isa(f.rhs, Tuple) ? collect(f.rhs) : [f.rhs]
     absorbed = findall(t -> isa(t, FunctionTerm{typeof(absorb)}), rhs)
     # Conditions based on panel and temporal indices and absorbed features

### 2019-07-03 src/solvers.jl

@@ -16,17 +16,35 @@
     w = transform(estimator, FrequencyWeights(wts))
     if !isempty(z)
         Z̃ = hcat(X, Z)
-        F = bunchkaufman!(Hermitian(Z̃' * Diagonal(w) * Z̃), true)
+        F = bunchkaufman(Hermitian(Z̃' * Diagonal(w) * Z̃), true, check = false)
+        bkr = count(x -> abs(x) ≥ √eps(), F.D)
+		if bkr < size(F, 2)
+            lin_ind = sort!(invperm(F.p)[1:bkr])
+            count(x -> lin_ind > size(X, 2) + 1) ≥ size(z, 2) ||
+                throw(ArgumentError("Insufficient number of instruments."))
+            Z̃ = Z̃[:,lin_ind]
+            F = bunchkaufman(Hermitian(Z̃' * Diagonal(w) * Z̃), true)
+        else
+            lin_ind = collect(1:size(F, 2))
+        end
         γ = F \ (Z̃' * Diagonal(w) * z)
         X̃ = hcat(X, Z̃ * γ)
     else
         X̃ = X
     end
-    F = bunchkaufman!(Hermitian(X̃' * Diagonal(w) * X̃), true)
+    F = bunchkaufman(Hermitian(X̃' * Diagonal(w) * X̃), true, check = false)
+    bkr = count(x -> abs(x) ≥ √eps(), F.D)
+    if bkr < size(F, 2)
+        lin_ind = sort!(invperm(F.p)[1:bkr])
+        X̃ = convert(Matrix{Float64}, X̃[:,lin_ind])
+        F = bunchkaufman(Hermitian(X̃' * Diagonal(w) * X̃), true)
+    else
+        lin_ind = collect(1:size(F, 2))
+    end
     β = F \ (X̃' * Diagonal(w) * y)
     Ψ = Hermitian(inv(F))
-    ŷ = isempty(z) ? X * β : hcat(X, z) * β
-    X, y, β, Ψ, ŷ, w, collect(1:size(X̃, 2))
+    ŷ = isempty(z) ? X̃ * β : hcat(X, z)[:,lin_ind] * β
+    X̃, y, β, Ψ, ŷ, w, lin_ind
 end
 @views function solve(estimator::ContinuousResponse,
                       X::AbstractMatrix{<:Number},
@@ -47,19 +65,37 @@ end
     w = transform(estimator, FrequencyWeights(wts))
[…]

### 2019-07-03 src/formula.jl
Added exception tests
- Exception tests
- Exclude non-positive weights

@@ -19,6 +19,10 @@ function decompose(f::FormulaTerm,
         throw(ArgumentError("Absorbing features is only implemented for least squares."))
     end
     pns = convert(Vector{Symbol}, filter!(!isnothing, union(termvars(f), [panel, time, wts])))
+    data = copy(data[pns])
+    if isa(wts, Symbol)
+        data[wts] = ifelse(data[wts] .≤ 0, missing, data[wts])
+    end
     data = dropmissing(data[pns])
     if isempty(absorbed)
         absorbed_features = ""

### 2019-07-03 test/runtests.jl

@@ -1,8 +1,49 @@
 using Econometrics, Test
-using Econometrics: Hermitian
-using RDatasets
-using RDatasets: CSV
+using Econometrics: ConvergenceException, Hermitian
+using RDatasets: categorical!, CSV, dataset, dropmissing, select
 
+# Exceptions
+@testset "Exceptions" begin
+	data = dataset("Ecdat", "Crime")
+	data.AvgSen2 = 2 * data.AvgSen
+	# Rank-deficient model
+	@test isa(fit(EconometricModel,
+			      @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + AvgSen2),
+				  data),
+			  EconometricModel)
+	@test isa(fit(RandomEffectsEstimator,
+				  @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris),
+				  data,
+				  panel = :County,
+				  time = :Year),
+			  EconometricModel)
+	# Model specifics
+	@test_throws(ArgumentError("The between estimator requires the panel identifier."),
+				 fit(BetweenEstimator,
+				 	 @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(Year)),
+					 data))
+	@test_throws(ArgumentError("Absorbing features is only implemented for least squares."),
+				 fit(BetweenEstimator,
+				 	 @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(Year)),
+					 data,
+					 panel = :County))
+	@test_throws(ArgumentError("The random effects estimator requires the panel and temporal identifiers."),
+				 fit(RandomEffectsEstimator,
+				 	 @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(Year)),
+					 data,
+					 panel = :County))
+	@test_throws(ArgumentError("Absorbing features is only implemented for least squares."),
+				 fit(RandomEffectsEstimator,
+				 	 @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(Year)),
+					 data,
+					 panel = :County,
+					 time = :Year))
+	data = dataset("datasets", "iris")
+	@test_throws(ConvergenceException,
+				 fit(EconometricModel,
+				 	 @formula(Species ~ SepalLength + SepalWidth),
+				 	 data))
+end
 # Linear Models
 @testset "Linear Models" begin
 	@testset "Balanced Panel Data" begin

### 2019-07-04 src/Econometrics.jl
HC VCE
HC VCE

@@ -5,50 +5,45 @@
 """
 module Econometrics
     using Base.Iterators: flatten
-    using DataFrames: AbstractDataFrame, DataFrame, dropmissing
+    using DataFrames: AbstractDataFrame, DataFrame, dropmissing,
+                      # CategoricalArrays
+                      AbstractCategoricalVector, categorical, levels, isordered
     using Distributions: cdf, ccdf, Categorical, Chisq, FDist, logpdf, Logistic, Normal,
                          pdf, TDist,
                          # Statistics
-                         mean, quantile, var,
-                         # StatsFuns
-                         softmax,
-                         # LinearAlgebra
-                         bunchkaufman, bunchkaufman!, cholesky!, diag, diagm, Diagonal,
-                         Hermitian, I, LowerTriangular, qr, UpperTriangular,
-                         # Printf
-                         @sprintf
+                         mean, quantile, var
     using FillArrays: Ones
-    using Optim: hessian!, optimize, minimizer, TwiceDifferentiable,
-                 # ForwardDiff
-                 ForwardDiff.Dual, ForwardDiff.value
+    using ForwardDiff: Dual, value
+    using LinearAlgebra: bunchkaufman, bunchkaufman!, cholesky!, diag, diagm,
+                         Diagonal, Hermitian, I, LowerTriangular, qr,
+                         UpperTriangular
+    using Optim: hessian!, optimize, minimizer, TwiceDifferentiable
     using Parameters: @unpack
+    using Printf: @sprintf
+    using StatsBase: aic, aicc, bic, harmmean, FrequencyWeights, CoefTable,
+                     ConvergenceException, Weights
+    using StatsFuns: softmax
     using StatsModels: AbstractContrasts, AbstractTerm, apply_schema, CategoricalTerm,
                        ConstantTerm, ContrastsMatrix, DummyCoding, @formula, FormulaTerm,
                        FunctionTerm, InterceptTerm, MatrixTerm, modelcols, schema, terms,
-                       termvars,
-                       # StatsBase
-                       aic, aicc, bic, harmmean, FrequencyWeights, CoefTable,
-                       ConvergenceException, Weights,
-                       # CategoricalArrays
-                       AbstractCategoricalVector, categorical, levels, isordered
+                       termvars
     import Base: show
-    import StatsModels: hasintercept, implicit_intercept,
-                        # StatsBase
[…]

### 2019-07-04 src/formula.jl

@@ -6,7 +6,8 @@ function decompose(f::FormulaTerm,
                    wts::Union{Nothing,Symbol},
                    panel::Union{Nothing,Symbol},
                    time::Union{Nothing,Symbol},
-                   estimator::Type{<:Union{EconometricsModel,ModelEstimator}})
+                   estimator::Type{<:Union{EconometricsModel,ModelEstimator}},
+                   vce::VCE)
     rhs = isa(f.rhs, Tuple) ? collect(f.rhs) : [f.rhs]
     absorbed = findall(t -> isa(t, FunctionTerm{typeof(absorb)}), rhs)
     # Conditions based on panel and temporal indices and absorbed features
@@ -25,16 +26,16 @@ function decompose(f::FormulaTerm,
     end
     data = dropmissing(data[pns])
     if isempty(absorbed)
-        absorbed_features = ""
         absorbed = Vector{Vector{Vector{Int}}}()
     elseif length(absorbed) == 1
+        vce ≥ HC2 &&
+            throw(ArgumentError("When absorbing features, only HC2-HC4 are unavailable."))
         absorbed = rhs[absorbed[1]]
         if isa(absorbed, AbstractVector)
             absorbed = unique(flatten(termvars(t) for t ∈ absorbed))
         else
             absorbed = termvars(absorbed)
         end
-        absorbed_features =
         absorbed = [ [ findall(isequal(l), data[dim]) for l ∈ levels(data[dim]) ] for dim ∈ absorbed ]
     else
         throw(ArgumentError("There can only be at most one absorb term"))
@@ -59,6 +60,8 @@ function decompose(f::FormulaTerm,
     if isa(f, FormulaTerm{<:CategoricalTerm})
         isa(iv.lhs, InterceptTerm{false}) ||
             throw(ArgumentError("Instrumental variables are only implemented for linear models."))
+        vce == OIM ||
+            throw(ArgumentError("Robust variance covariance estimators only available for continous response models."))
         if isordered(data[f.lhs.sym])
             any(x -> isa(x, InterceptTerm{false}), f.rhs.terms) &&
                 throw(ArgumentError("This estimator requires an intercept term."))

### 2019-07-04 src/main.jl

@@ -19,7 +19,8 @@ mutable struct EconometricModel{E<:ModelEstimator,
                                 Ŷ<:AbstractVecOrMat{<:Float64},
                                 N<:Tuple{<:Union{<:AbstractVector{<:AbstractString},
                                                  <:AbstractString},
-                                         <:AbstractVector{<:AbstractString}}} <: EconometricsModel
+                                         <:AbstractVector{<:AbstractString}},
+                                VC<:Union{<:Type{<:VCE},<:VCE}} <: EconometricsModel
     estimator::E
     f::F
     data::DataFrame
@@ -31,6 +32,7 @@ mutable struct EconometricModel{E<:ModelEstimator,
     ŷ::Ŷ
     vars::N
     iv::Int
+    vce::VC
 end
 function show(io::IO, obj::EconometricModel{<:LinearModelEstimators})
     show(io, obj.estimator)
@@ -50,6 +52,7 @@ function show(io::IO, obj::EconometricModel{<:LinearModelEstimators})
         end
     end
     println(io, string("Formula: ", fs))
+    println(io, "Variance Covariance Estimator: $(obj.vce)")
     show(io, coeftable(obj))
 end
 function show(io::IO, obj::EconometricModel{<:ContinuousResponse})
@@ -83,6 +86,7 @@ function show(io::IO, obj::EconometricModel{<:ContinuousResponse})
         fs = replace(fs, r"(^.*?) ~ " => s"\1 ~ 1 + ")
     end
     println(io, string("Formula: ", fs))
+    println(io, "Variance Covariance Estimator: $(obj.vce)")
     show(io, coeftable(obj))
 end
 function show(io::IO, obj::EconometricModel{<:NominalResponse})
@@ -133,11 +137,12 @@ function fit(estimator::Type{<:Union{EconometricModel,ModelEstimator}},
              contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}}(),
              weights::Union{Nothing,Symbol} = nothing,
              panel::Union{Nothing,Symbol} = nothing,
-             time::Union{Nothing,Symbol} = nothing)
+             time::Union{Nothing,Symbol} = nothing,
+             vce::VCE = OIM)
     data, exogenous, iv, estimator, X, y, z, Z, wts =
[…]

### 2019-07-04 src/statsbase.jl

@@ -3,7 +3,6 @@ dispersion(obj::EconometricModel{<:Union{NominalResponse,OrdinalResponse}}) = fa
 isiv(obj::EconometricModel{<:LinearModelEstimators}) = obj.iv > 0
 coef(obj::EconometricModel) = obj.β
 coefnames(obj::EconometricModel) = obj.vars
-# StatsBase.confint(obj::StatisticalModel) = error("coefint is not defined for $(typeof(obj)).")
 deviance(obj::EconometricModel) = -2loglikelihood(obj)
 deviance(obj::EconometricModel{<:LinearModelEstimators}) =
 	weights(obj) |>
@@ -77,11 +76,39 @@ function adjr2(obj::EconometricModel{<:LinearModelEstimators})
 end
 informationmatrix(obj::EconometricModel; expected::Bool = true) = obj.Ψ
 vcov(obj::EconometricModel) = informationmatrix(obj)
-vcov(obj::EconometricModel{<:LinearModelEstimators}) =
-	deviance(obj) / dof_residual(obj) * informationmatrix(obj)
-stderror(obj::EconometricModel) = sqrt.(diag(vcov(obj)))
-confint(obj::EconometricModel, α = 0.05) =
-    stderror(obj) * quantile(TDist(dof_residual(obj)), 1 - α / 2) |>
+function vcov(obj::EconometricModel{<:LinearModelEstimators})
+	vcov(obj::EconometricModel{<:LinearModelEstimators}, obj.vce)
+end
+function vcov(obj::EconometricModel{<:LinearModelEstimators}, vce::VCE)
+	vce == OIM &&
+		return deviance(obj) / dof_residual(obj) * informationmatrix(obj)
+	X = modelmatrix(obj)
+	Ψ = informationmatrix(obj)
+	û = residuals(obj)
+	m = nobs(obj)
+	k = dof(obj) - hasintercept(obj)
+	p = dof_residual(obj)
+	λ = vce == HC1 ? m / p : 1
+	if vce == HC0 || vce == HC1
+		ũ = û.^2
+	else
+		h = leverage(obj)
+		if vce == HC2
+			ũ = û.^2 ./ (1 .- h)
+		elseif vce == HC3
+			ũ = û.^2 ./ (1 .- h).^2
+		elseif vce == HC4
+			ũ = û.^2 ./ (1 .- h).^min.(4, m / k * h)
+		end
+	end
[…]

### 2019-07-04 src/structs.jl

@@ -98,3 +98,12 @@ function show(io::IO, estimator::OrdinalResponse)
     println(io, "Probability Model for Ordinal Response")
     println(io, "Categories: $(join(estimator.categories, " < "))")
 end
+# Variance-covariance Estimators
+@enum VCE begin
+    OIM = -1
+    HC0 = 0
+    HC1 = 1
+    HC2 = 2
+    HC3 = 3
+    HC4 = 4
+end

### 2019-07-04 src/wald.jl

@@ -1,6 +1,6 @@
-function wald(obj::EconometricModel)
+function wald(obj::EconometricModel, vce::VCE = obj.vce)
     β = coef(obj)
-    V = vcov(obj)
+    V = vcov(obj, vce)
 	k = length(β) - 1
 	rdf = dof_residual(obj)
 	R = hasintercept(obj) ? hcat(zeros(k), I) : I

### 2019-07-04 test/runtests.jl

@@ -1,7 +1,6 @@
 using Econometrics, Test
 using Econometrics: ConvergenceException, Hermitian
-using RDatasets: categorical!, CSV, dataset, dropmissing, select
-
+using RDatasets: categorical, categorical!, CSV, dataset, dropmissing, levels!, select
 # Exceptions
 @testset "Exceptions" begin
 	data = dataset("Ecdat", "Crime")
@@ -43,6 +42,17 @@ using RDatasets: categorical!, CSV, dataset, dropmissing, select
 				 fit(EconometricModel,
 				 	 @formula(Species ~ SepalLength + SepalWidth),
 				 	 data))
+	# Robust variance covariance estimators
+	@test_throws(ArgumentError("Robust variance covariance estimators only available for continous response models."),
+				 fit(EconometricModel,
+				 	 @formula(Species ~ SepalLength + SepalWidth),
+				 	 data,
+					 vce = HC1))
+	@test_throws(ArgumentError("When absorbing features, only HC2-HC4 are unavailable."),
+				 fit(EconometricModel,
+				 	 @formula(SepalLength ~ SepalLength + absorb(Species)),
+				 	 data,
+					 vce = HC2))
 end
 # Linear Models
 @testset "Linear Models" begin
@@ -53,7 +63,7 @@ end
     	model = fit(EconometricModel,
                 	@formula(CRMRTE ~ PrbConv + AvgSen + PrbPris),
                 	data)
[…]

### 2019-07-04 dev/search_index.js
build based on 90c9290

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"#Econometrics-1","page":"Econometrics","title":"Econometrics","text":"","category":"section"},{"location":"#Setup-1","page":"Econometrics","title":"Setup","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"using Econometrics, CSV, RDatasets","category":"page"},{"location":"#Continuous-Response-Models-1","page":"Econometrics","title":"Continuous Response Models","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"data = RDatasets.dataset(\"Ecdat\", \"Crime\") |>\n  (data -> select(data, [:County, :Year, :CRMRTE, :PrbConv, :AvgSen, :PrbPris]))\nfirst(data, 6)","category":"page"},{"location":"#Pooling-1","page":"Econometrics","title":"Pooling","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris),\n            data)","category":"page"},{"location":"#Between-1","page":"Econometrics","title":"Between","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(BetweenEstimator,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris),\n            data,\n            panel = :County)","category":"page"},{"location":"#Within-1","page":"Econometrics","title":"Within","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(County)),\n            data)","category":"page"},{"location":"#Within-(two-ways)-1","page":"Econometrics","title":"Within (two-ways)","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(EconometricModel,\n            @formula(CRMRTE ~ PrbConv + AvgSen + PrbPris + absorb(County + Year)),\n            data)","category":"page"},{"location":"#Random-1","page":"Econometrics","title":"Random","text":"","category":"section"},{"location":"#","page":"Econometrics","title":"Econometrics","text":"model = fit(RandomEffectsEstimator,\n            @formula(CRMRTE ~ PrbCon
[…]

### 2019-07-04 src/Econometrics.jl
DataFrames proof
Using getproperty now.

@@ -5,7 +5,7 @@
 """
 module Econometrics
     using Base.Iterators: flatten
-    using DataFrames: AbstractDataFrame, DataFrame, dropmissing,
+    using DataFrames: AbstractDataFrame, DataFrame, dropmissing, select,
                       # CategoricalArrays
                       AbstractCategoricalVector, categorical, levels, isordered
     using Distributions: cdf, ccdf, Categorical, Chisq, FDist, logpdf, Logistic, Normal,

### 2019-07-04 src/formula.jl

@@ -20,11 +20,11 @@ function decompose(f::FormulaTerm,
         throw(ArgumentError("Absorbing features is only implemented for least squares."))
     end
     pns = convert(Vector{Symbol}, filter!(!isnothing, union(termvars(f), [panel, time, wts])))
-    data = copy(data[pns])
+    data = select(data, pns)
     if isa(wts, Symbol)
-        data[wts] = ifelse(data[wts] .≤ 0, missing, data[wts])
+        data[wts] = ifelse(getproperty(data, wts) .≤ 0, missing, getproperty(data, wts))
     end
-    data = dropmissing(data[pns])
+    data = dropmissing(select(data, pns, copycols = false))
     if isempty(absorbed)
         absorbed = Vector{Vector{Vector{Int}}}()
     elseif length(absorbed) == 1
@@ -36,7 +36,7 @@ function decompose(f::FormulaTerm,
         else
             absorbed = termvars(absorbed)
         end
-        absorbed = [ [ findall(isequal(l), data[dim]) for l ∈ levels(data[dim]) ] for dim ∈ absorbed ]
+        absorbed = [ [ findall(isequal(l), getproperty(data, dim)) for l ∈ levels(getproperty(data, dim)) ] for dim ∈ absorbed ]
     else
         throw(ArgumentError("There can only be at most one absorb term"))
     end
@@ -62,7 +62,7 @@ function decompose(f::FormulaTerm,
             throw(ArgumentError("Instrumental variables are only implemented for linear models."))
         vce == OIM ||
             throw(ArgumentError("Robust variance covariance estimators only available for continous response models."))
-        if isordered(data[f.lhs.sym])
+        if isordered(getproperty(data, f.lhs.sym))
             any(x -> isa(x, InterceptTerm{false}), f.rhs.terms) &&
                 throw(ArgumentError("This estimator requires an intercept term."))
             estimator = OrdinalResponse(f.lhs.contrasts)
@@ -74,7 +74,7 @@ function decompose(f::FormulaTerm,
         throw(ArgumentError("The random effects estimator requires an intercept term."))
     end
     if isa(exogenous.lhs, CategoricalTerm)
-        y = data[exogenous.lhs.sym]
+        y = getproperty(data, exogenous.lhs.sym)
         X = modelcols(exogenous.rhs, data)
         if isordered(y)
             X = X[:,2:end]
[…]

### 2019-07-04 test/runtests.jl

@@ -1,6 +1,6 @@
 using Econometrics, Test
 using Econometrics: ConvergenceException, Hermitian
-using RDatasets: categorical, categorical!, CSV, dataset, dropmissing, levels!, select
+using CSV, RDatasets
 # Exceptions
 @testset "Exceptions" begin
 	data = dataset("Ecdat", "Crime")
@@ -223,13 +223,14 @@ end
 end
 # Ordinal Models
 @testset "Ordinal Models" begin
-	data = dataset("Ecdat", "Kakadu")[[:RecParks, :Sex, :Age, :Schooling]]
+	data = dataset("Ecdat", "Kakadu") |>
+		(data -> select(data, [:RecParks, :Sex, :Age, :Schooling]))
 	data.RecParks = convert(Vector{Int}, data.RecParks)
 	data.RecParks = levels!(categorical(data.RecParks, ordered = true), collect(1:5))
 	model = fit(EconometricModel,
               	@formula(RecParks ~ Age + Sex + Schooling),
               	data)
-  	@test sprint(show, model) == "Probability Model for Ordinal Response\nCategories: 1 < 2 < 3 < 4 < 5\nNumber of observations: 1827\nNull Loglikelihood: -2677.60\nLoglikelihood: -2657.40\nR-squared: 0.0075\nLR Test: 40.42 ∼ χ²(3) ⟹ Pr > χ² = 0.0000\nFormula: RecParks ~ Age + Sex + Schooling\n──────────────────────────────────────────────────────────────────────────────────────────\n                          PE          SE        t-value  Pr > |t|         2.5%       97.5%\n──────────────────────────────────────────────────────────────────────────────────────────\nAge                  0.00943647  0.00254031    3.71469     0.0002   0.00445424   0.0144187\nSex: male           -0.0151659   0.0846365    -0.179188    0.8578  -0.181161     0.150829 \nSchooling           -0.103902    0.0248742    -4.17711     <1e-4   -0.152687    -0.0551174\n(Intercept): 1 | 2  -2.92405     0.191927    -15.2352      <1e-48  -3.30047     -2.54763  \n(Intercept): 2 | 3  -1.54922     0.171444     -9.03632     <1e-18  -1.88547     -1.21297  \n(Intercept): 3 | 4  -0.298938    0.166904     -1.79108     0.0734  -0.626281     0.0284051\n(Intercept): 4 | 5   0.669835    0.167622      3.9961      <1e-4    0.341083     0.998587 \n──────────────────────────────────────────────────────────────────────────────────────────"
[…]

### 2019-07-05 paper/paper.tex
Updates from Overleaf

@@
 \usepackage[hypcap=true]{caption}
-%\captionsetup[table]{labelfont=bf,textfont=it}
-%\captionsetup[figure]{labelfont=bf,textfont=it}
 \usepackage{booktabs, multirow, array, tabularx, floatrow, cellspace, threeparttable}
@@
     pdfauthor   = {José Bayoán Santiago Calderón},
-    pdfkeywords = {Julia, Econometrics, Statistical Software, Software Validation},
+    pdfkeywords = {Julia, Econometrics, Regression Analysis, Panel Data, Generalized Linear Models, Discrete Choice Models, Instrumental Variables Estimation, Variable Absorption, Software Validation},
     colorlinks  = true,
@@
 
-% An abstract with at most 600 characters, written in plain English with no symbol nor formula.
-% A list of at most 10 keywords as specified in the template, separated by commas and written in plain English.
-% Compared to an extended abstract, a full paper presents more of the background and context motivating the work.
-It compares the work to other approaches taken in the field and gives some additional insights on the talk.
-Use cases back up the work by showing how it can be used.
-
 Econometrics.jl is a package for econometrics analysis.
-It provides a series of most common routines for applied econometrics such as models for continuous, nominal, and ordinal outcomes, longitudinal estimators, variable absorption, weights, rank deficient, and robust variance covariance estimators.
+It provides a series of most common routines for applied econometrics such as models for continuous, nominal, and ordinal outcomes, longitudinal estimators, variable absorption, and support for convenience functionality such as weights, rank deficient, and robust variance covariance estimators.
+This study complements the package through a discussion of the motivation, placing the contribution within the Julia ecosystem and econometrics software in general, and provides insights on current gaps and ways the Julia ecosystem can evolve.
 
@@
 
-This study will: (1) provide an overview of common routines and their statistical and technical requirements, (2) provide an overview of tools available with their peculiarities, (3) discuss design decisions in the development of these tools, and (4) showcase \textit{Econometrics.jl} as a new tool for applied work.
+This study has four core sections.
+The first surveys what are some commonly used functionality for econometrics analysis.
+The second provides an overview of the current state of these within the Julia ecosystem including current tools and gaps.
+The third provides a comprehensive summary of the functionality provided by the new package, Econometrics.jl, and next steps.
+Lastly, I provide insights on how the Julia ecosystem can evolve from my experience developing the new tool.
 
-Regression models may be used for several purposes.
-These may provide a basis for prediction models, causal inference, etc.
-Common targets include confidence intervals of the parameters estimates, joint-significance of a feature, out-of-sample predictive performance, and others.
-In other words, obtaining the estimates of a model is usually only part of the task.
-In order to judge a model, one may require to perform diagnostics and tests to justify potential conclusions for an analysis.
+Regression analysis is a core tool used to understand the relation among variables.
+For example, understanding these relationships can provide insights into causal relations or as a basis to develop predictive models.
+In the realm of statistical inference from regression analysis, one may be interested in common targets such as confidence intervals of the parameters estimates, joint-significance of features, out-of-sample predictive performance, and others.
+Moreover, most models make certain assumptions which can be tested through statistical tests or model diagnostics which provide confidence in the estimation and results.
 
-Regression analysis is at the core of applied econometrics.
-It can be challenging to grasp the extent what makes up the broad term of regression analysis.
-The following describes a very brief survey of what this technique might entail.
+Regression analysis is a broad term that encompasses a wide variety of estimators and models.
+What follows is a brief summary of some of the many components that may fall within the concept.
 Regression analysis can be used for both observational and experimental settings and it allows great flexibility for a multitude of applications.
 The main idea is to find estimates for model parameters to optimize some objective such as the likelihood in maximum likelihood estimation (MLE).
-Other potential objectives include restricted maximum likelihood (REML) or a Bayesian approach such as maximum a posteriori probability (MAP).
+Other potential objectives include restricted maximum likelihood (REML) or a (Quasi-)Bayesian approach such as maximum a posteriori probability (MAP).
 One framework is the generalized linear model (GLM) which use a linear predictor that is mapped through a link function to a distribution modeling the response.
@@
 Some educated guesses may be well justified such as ordinary least squares being more widely used than spatially-weighted regressions.
-In order to avoid speculation, I defer to a reasonable assumption that the most common estimators are those usually taught in academic programs and available in widely used software similarly to \cite{Renfro_2009}.
-Most programs teach tools to address the most common response types: continuous, count, rates, nominal, and ordinal outcomes.
-Hence, some routines might be linear models, Poisson/negative binomial, multinomial logistic regression, and ordinal logistic regression with proportional odds assumption.
+In order to avoid speculation, I defer to a reasonable assumption that the most common estimators are those usually taught in academic programs and available in widely used software \cite{Renfro_2009}.
+Most programs teach tools to address the most common response types: continuous, count / rates, nominal, ordinal, and duration outcomes.
+This suggests some common models may include linear models, Poisson/negative binomial, multinomial logistic regression, and ordinal logistic regression with proportional odds assumption.
 Topics in time series and panel data are usually offered in most programs.
-Perhaps the most common topic is short panels (many units of observations through relatively small number of repeated observations).
+Perhaps, the most common topic is short panels (i.e., many units of observations and relatively small number of repeated observations).
 Common estimators include pooling, first-difference, fixed effects / within estimator, and one-way random effects.
@@
 
-\cite{Renfro_2009} surveyed the functionality of 24 alternatives for common econometrics routines.
+Previous work have surveyed the functionality of 24 alternatives for common econometrics routines \cite{Renfro_2009}.
 Throughout the history of econometrics software, alternatives have risen and fallen in following.
@@
 Functionality may be provided by the base/standard libraries in the statistical software environment, as a product such as a toolkit or user contributed such as a module/package that is distributed.
-Some examples of user-contributed functionality include the \textit{reghdfe} Stata module and a series of R packages such as \textit{MASS} \cite{MASS}, \textit{lmtest} \cite{lmtest}, \textit{sandwich} \cite{sandwich}, \textit{plm} \cite{plm}, and \textit{mlogit} \cite{mlogit}.
+Some examples of user-contributed functionality include the reghdfe Stata module and a series of R packages such as MASS \cite{MASS}, lmtest \cite{lmtest}, sandwich \cite{sandwich}, plm \cite{plm}, and mlogit \cite{mlogit}.
 
 The Julia language \cite{Bezanson_Edelman_Karpinski_Shah_2017} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks.
-The following sections describe commons estimators, the Julia ecosystem supporting tools, and Econometrics.jl which provides further functionality.
 
@@
 However, a Cholesky decomposition would still be required if the information matrix is desired.
-The solution method with QR decomposition is delineated in equation \ref{QR}.\footnote{The \textbackslash refers multiplication of $b$ by the inverse of $A$ on the left}
+The solution method with QR decomposition is delineated in equation \ref{QR}.\footnote{The (\textbackslash)\ refers to multiplication of $b$ by the inverse of $A$ on the left.}
 
 The case for the Cholesky decomposition follows closely and without loss of generality other variants could be used such as Bunch-Kaufman decomposition or the upper triangular form ($U^{\top}U$).
-The QR decomposition is more numerically stable, but more expensive than Cholesky.\footnote{$\mathcal{O}\left(n^{3}\right) > \mathcal{O}\left(2mn^{2}-\frac{2}{3}2n^{3}\right)$ where the matrix has $m$ rows and $n$ columns}.
-Equation \ref{Cholesky} delineates the solution method with Cholesky decomposition.
-Since the information matrix is an important component, Bunch-Kaufman decomposition, a Cholesky variant, is the preferred method used in \textit{Econometrics.jl}.
+The QR decomposition is more numerically stable, but more expensive than Cholesky.\footnote{$\mathcal{O}\left(n^{3}\right) > \mathcal{O}\left(2mn^{2}-\frac{2}{3}2n^{3}\right)$ where the matrix has $m$ rows and $n$ columns.} Equation \ref{Cholesky} delineates the solution method with Cholesky decomposition.
+Since the information matrix is an important component, Bunch-Kaufman decomposition, a Cholesky variant, is the preferred method used in Econometrics.jl.
 
@@
 Moreover, some parameters may not be consistently estimated in certain contexts.
-For example, individual fixed effects are not consistently estimated when there is a fixed length for the panels (i.e., more observations implies more parameters).
+For example, individual fixed effects are not consistently estimated when there is a fixed length for the panels (i.e., more observations implies more parameters a type of curse of dimensionality).
 
@@
 There are several methods to obtain a suitable alternative regression and these are not unique.
-\cite{reghdfe} presents several approaches to solving these problem including specialized methods in certain applications.
-Some implementations include \textit{reghdfe}, Stata module, and Matthieu Gomez \textit{FixedEffectModels.jl} package.
+Stata's module reghdfe \cite{reghdfe} presents several approaches to solving these problem including specialized methods in certain applications.
+Some implementations include Stata module reghdfe and the FixedEffects.jl package.
 The two most common approaches are solving for the residuals through a sparse least-squares problems such as with LSMR \cite{LSMR} or using some variant for the method of alternating projections.
@@
 The method of alternating projections is able to preserve under certain conditions artifacts of the original regression such as obtaining the same estimate for the intercept even though it is not particularly meaningful.
+Using the original response and the invariant residuals allows to recover the fitted values of the original model.
 
@@
 In the case of the random effects model, the within and between models are estimated using 2SLS to obtain the error component estimates.
-After applying the random effects transformation to each model term the 2SLS process is employed in the final regression model à la \cite{BV_1987}.
+After applying the random effects transformation to each model term the 2SLS process is employed in the final regression model \cite{BV_1987}.
 
@@
 where $F$ is the cumulative distribution function of the logistic distribution with zero location and unit scale, $\eta$ is the linear projection, and $\alpha_{k}$ is the threshold for lower threshold \cite{ologit}.
-The log-likelihood function and the gradient are passed to the \textit{Optim.jl} framework \cite{Optim} using \textit{ForwardDiff.jl} \cite{ForwardDiff} forward mode automatic differentiation (AD) for the Newtonian solver.
+The log-likelihood function and the gradient are passed to the Optim.jl framework \cite{Optim} using ForwardDiff.jl \cite{ForwardDiff} forward mode automatic differentiation (AD) for the Newtonian solver.
 
@@
 These values are then compared against a chosen tolerance and the column of the term is deemed linearly independent if the values are greater than the tolerance.
+
 Note that Cholesky, QR, and Bunch-Kaufman decomposition allow to identify which columns are independent while singular values only allow to determine the rank.
 It may be arbitrary to choose among linearly dependent features.
-An additional level of complexity in probability models is the issue of linearly separability.
-\cite{Konis_2007} provides an overview of potential approaches to identifying the issue.
+An additional level of complexity in probability models is the issue of linearly separability for probability models \cite{Konis_2007}.
 
@@
 
-\textit{StatsBase.jl} builds on top of Statistics.jl (standard library) to provide additional statistical functionality.
-One which includes the abstraction for Statistical Models (and Regression models which inherit from the former).
+StatsBase.jl builds on top of Statistics.jl (standard library) to provide additional statistical functionality.
+One which includes the abstraction for Statistical Models (and Regression models which inherits from the former).
 It provides a simple and powerful API for the whole Julia ecosystem to use.
@@
 
-\textit{Tables.jl} provide an interface for tabular data.
+Tables.jl provide an interface for tabular data.
 This API allows users to choose from various solutions the tabular data implementation of their choosing without having to worry that their choice will limit potential functionality.
-Many tabular implementations such as \textit{DataFrames.jl} provide robust functionality to many routines such as handling categorical features, dates/time, missing values, reshaping data, split/apply operations, and others.
+Many tabular implementations such as DataFrames.jl provide robust functionality to many routines such as handling categorical features, dates/time, missing values, reshaping data, split/apply operations, and others.
 Users need not to worry about any I/O issues as a rich array of options exist for importing and exporting across different file formats such as delimiter-separated values, JSON, Feather, HDF5, MATLAB, Stata, SPSS, SAS, and R.
 
-\textit{StatsModels.jl} is a package that provides the means to go from data to model terms.
-It provides the formulae language (e.g., similar syntax to R's formulae syntax).
+StatsModels.jl is a package that provides the means to go from data to model terms.
+It provides the formulae language (e.g., similar to R's formulae syntax).
 A model is then build using a formula, data, and additional model specific arguments.
@@
 
-The regression analysis ecosystem in Julia has \textit{GLM.jl} as its flagship.
-\textit{GLM.jl} provides the typical functionality for fitting generalized linear models through Fisher scoring.
+The regression analysis ecosystem in Julia has GLM.jl as its flagship.
+GLM.jl provides the typical functionality for fitting generalized linear models through Fisher scoring.
 This includes linear models, Poisson/Negative Binomial, Logit/Probit, and other non-canonical link models.
-\textit{CovarianceMatrices.jl} provides various variance covariance estimators for \textit{GLM.jl} models à la R's \textit{sandwich} package.
-\textit{LinearMixedModels.jl} \cite{LinearMixedModels} extends \textit{GLM.jl} for mixed-effects models.
-\textit{FixedEffectModels.jl} provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la \textit{reghdfe}.
-\textit{Survival.jl} provides a series of estimators for duration models.
+CovarianceMatrices.jl provides various variance covariance estimators for GLM.jl models à la R's
+sandwich package.
+LinearMixedModels.jl \cite{LinearMixedModels} extends GLM.jl for mixed-effects models.
+FixedEffectModels.jl provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la reghdfe.
+Survival.jl provides a series of estimators for duration models.
 Two major gaps in the ecosystem include estimating nominal and ordinal response models (i.e., discrete choice) with more than two alternatives and support for longitudinal estimators.
@@
 
-\textit{Econometrics.jl} is a package for performing several common econometrics routines in the Julia language.
+Econometrics.jl is a package for performing several common econometrics routines in the Julia language.
 It aims to provide the following functionality for two major gaps in the ecosystem, longitudinal estimators and discrete choice models.
@@
 However, the development of this package serves multiple purposes beyond the immediate effect.
-As the statistics ecosystem evolves and matures, \textit{Econometrics.jl} aims to serve as inspiration and an alternative to design decisions, standards, and option for user.
+As the statistics ecosystem evolves and matures, Econometrics.jl aims to serve as inspiration and an alternative to design decisions, standards, and option for users and developers.
 
@@
 
-For linear models, the examples use the crime data set from \cite{Crime}.
+For linear models, the examples use a crime dataset \cite{Crime}.
 The data set is a balanced longitudinal data set with 90 counties in North Carolina from 1981 to 1987.
 The outcome variable is the crime rate and the explanatory variables include the probability of conviction, average sentence, and probability of prison sentence.
-Estimating the pooling estimator or between estimators can be accomplished as in figure \vref{estimator_pooling} and \vref{estimator_between}.
+Estimating the pooling estimator or the between estimator can be accomplished as in figure \vref{estimator_pooling} and \vref{estimator_between}.
 Table \vref{poberes} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.
@@
 
-The fixed effects model or within estimator can be estimated as in figure \vref{withinmodel} which estimates the panel effects and the two-ways fixed effects model (i.e., fixed effects for time dimension as well).
+The fixed effects model or within estimator can be estimated as in figure \vref{withinmodel} which a two-ways fixed effects model (i.e., fixed effects for panel and time dimensions).
 Table \vref{withinres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.
@@
 \begin{figure}[hbpt]
-	\includegraphics[max width=\linewidth,center]{estimator_within}
-	\caption{Estimation of the within estimator}
+	\includegraphics[max width=\linewidth,center]{estimator_fe}
+	\caption{Estimation of the within estimator with multiple fixed effects}
 	\label{withinmodel}
@@
 
-\begin{figure}[hbpt]
-	\includegraphics[max width=\linewidth,center]{estimator_within2}
-	\caption{Estimation of the within estimator with multiple fixed effects}
-	\label{within2model}
-\end{figure}
+\newpage
 
-The random effects model can be estimated with similar syntax by including the \textit{PID} (panel identifier) and \textit{TID} (temporal identifier) tags such as in figure \vref{random} which shows estimating a random effects model as well as its instrumental variables counterpart.
+The random effects model can be estimated as in figure \vref{random} which shows estimating a random effects model with instrumental variables.
 Table \vref{xtregres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata's reghdfe module, and R's plm package.
@@
 \begin{figure}[hbpt]
-	\includegraphics[max width=\linewidth,center]{estimator_re}
+	\includegraphics[max width=\linewidth,center]{estimator_ivre}
 	\caption{Estimation of the random effects model}
@@
 For example, advances in econometrics are rarely widely adopted without buy-in from software developers.
-The following discussions will survey survey some of the decisions relevant to \textit{Econometrics.jl}.
+The following discussions will survey some of the decisions relevant to Econometrics.jl.
 
@@
 The trade-off occurs when users may encounter a specification that while uncommon it may be the correct one for that particular model.
-Currently, \textit{Econometrics.jl} takes a conservative approach that provides ``dummy-proof'' experience as well as ease of use.
-For example, rather than requiring users to specify the model, the estimator is inferred based on the type of the response and information provided.
-Other examples of this approach include making model statistics such as promoting the coefficient of determination to a pseudo-version for non-linear models (a generalization of the linear case), but providing a \textit{not a number} (NaN) value for instrumental variable models or those that do not include an intercept.
-Similarly, the software will promote terms to full rank as required and inform of the behavior.
+Currently, Econometrics.jl takes a conservative approach that provides ``dummy-proof'' experience as well as ease of use.
+For example, rather than requiring users to specify the model, the estimator is inferred based on the type of the response and information provided as long as it is unambiguous.
+Other examples of this approach include auto-promoting model statistics such as the coefficient of determination to a pseudo-version for non-linear models (a generalization of the linear case), but providing a not a number (NaN) value for instrumental variable models or those that do not include an intercept.
+Similarly, the software will promote terms to full rank as required.
+The formula term and coefficient table provide all the information needed to figure which if any feature was suppressed.
 
@@
 The test might include components such as the residual degrees of freedom, the information matrix, residuals, and score.
-Many implementations might access internals of one particular implementation and compute these such as obtaining the model matrix, response and coefficients to compute the residuals.
-This behavior would produce incorrect estimates in cases of instrumental variable as the fitted / linear projection should not use the model matrix, but replace the projection of endogenous features with their actual values.
-A better approach would be to request the response and fitted values to compute the residuals.
-This approach is less prone to errors, but it can be more robust by calling residuals directly.
-Specifying precise components can alleviate risk of errors or relying on assumptions such as whether the components are weighted or should be weighted for the procedure.
+Currently, some packages rely on accessing internal components specific to those implementations rather than an implementation agnostic interface.
+A common public API would also allow to catch context specific instances of improper behavior.
 
@@
 For example, software may differs on how it computes the degrees of freedom for instrumental variables or absorbed variables depending on the context (e.g., main regression or auxiliary regression for estimating error components).
-Refinements and robustness checks can also contribute to a better analysis such as verifying gaps for time variant operations such as first-difference or purging singletons and other degree of freedom adjustments à la \cite{Singletons}.
+Refinements and robustness checks can also contribute to a better analysis such as verifying gaps for time variant operations such as in first-difference or purging singletons and other degree of freedom adjustments \cite{Singletons}.
 
@@
 
-\textit{Econometrics.jl} adopts the best practices standards for open-source statistical software.
+Econometrics.jl adopts the best practices standards for open-source statistical software.
 These include adhering to semantic versioning (semver) for descriptive versioning, continuous integration for development, software validation through a comprehensive code coverage and test suite, and lastly online hosted documentation for the public API.
@@
 
-\textit{Econometrics.jl} is a new addition to the Julia ecosystem that brings highly demanded functionality concerning longitudinal estimators and discrete choice models.
+Econometrics.jl is a new addition to the Julia ecosystem that brings highly demanded functionality concerning longitudinal estimators and discrete choice models.
 This study serves as a complement to the software documentation providing context to the development, design considerations, and roadmap of the project.
@@
 Community contributions and feedback are highly encouraged in order to best continue developing the project.
-The release will be available at the Github repository and licensed under a permissive license.
+Some features I would like the project to support in the future include more advanced estimators such as: (1) choice-variant categorical response models, (2) count/rate models such as zero-inflated, and (3) censored/truncated response models.
+Econometrics.jl is ISC licensed and available at the GitHub repository.
 
-\vfill
+\section{Acknowledgement}
+
+This research benefited from support from the National Science Foundation and the AEA Mentoring Program: NSF Awards 1357478 \& 1730651.
 

### 2019-08-13 docs/make.jl
Public API

@@ -12,7 +12,8 @@ makedocs(format = Documenter.HTML(assets = ["assets/custom.css"]),
          sitename = "Econometrics.jl",
          pages = ["Introduction" => "index.md",
                   "Getting Started" => "getting_started.md",
-                  "Estimators" => "estimators.md"]
+                  "Estimators" => "estimators.md",
+                  "Public API" => "public_api.md"]
     )
 
 deploydocs(repo = "github.com/Nosferican/Econometrics.jl.git")

### 2019-08-13 src/main.jl

@@ -6,11 +6,21 @@
                      time::Union{Nothing,Symbol} = nothing,
                      estimator::ModelEstimator = ModelEstimator)
 
-    Use fit(EconometricModel, f, data, contrasts = contrasts)
-    Formula has syntax: @formula(response ~ exogenous + (endogenous ~ instruments))
-    For absorbing categorical features use the term `absorb(features)`
-    For the between estimator use the term `between(features)`
-    For the one-way random effects model use the terms `PID(pid) + TID(tid)`
+Formula has syntax:
+
+    @formula(response ~ exogenous + (endogenous ~ instruments) + absorb(highdimscontrols))
+
+Data must implement the Tables.jl API and use CategoricalArrays (CategoricalVector)
+
+Weights are taken as `StatsBase.FrequencyWeights`
+
+Panel and time indicators are used for longitudinal estimators
+
+# Examples
+
+    model = fit(EconometricModel, formula, data, kwargs...)
+    model = fit(BetweenEstimator, formula, data, panel = :panel, kwargs...)
+    model = fit(RandomEffectsEstimator, formula, data, panel = :panel, time = :time, kwargs...)
 """
 mutable struct EconometricModel{E<:ModelEstimator,
                                 F<:FormulaTerm,

### 2019-08-13 paper/paper.tex

@@
 The first surveys what are some commonly used functionality for econometrics analysis.
-The second provides an overview of the current state of these within the Julia ecosystem including current tools and gaps.
+The second provides an overview of the current state of these within the Julia \cite{Bezanson_Edelman_Karpinski_Shah_2017} ecosystem including current tools and gaps.
 The third provides a comprehensive summary of the functionality provided by the new package, Econometrics.jl, and next steps.
@@
 For example, understanding these relationships can provide insights into causal relations or as a basis to develop predictive models.
-In the realm of statistical inference from regression analysis, one may be interested in common targets such as confidence intervals of the parameters estimates, joint-significance of features, out-of-sample predictive performance, and others.
+In the realm of statistical inference, one may be interested in common targets such as confidence intervals of the parameters estimates, joint-significance of features, out-of-sample predictive performance, and others.
 Moreover, most models make certain assumptions which can be tested through statistical tests or model diagnostics which provide confidence in the estimation and results.
@@
 
-Out of the many potential tools practitioners may require, what are some of the most common?
+Of the many potential tools practitioners may require, what are some of the most common?
 Not every estimator is as widely accessible or commonly used.
@@
 Some examples of user-contributed functionality include the reghdfe Stata module and a series of R packages such as MASS \cite{MASS}, lmtest \cite{lmtest}, sandwich \cite{sandwich}, plm \cite{plm}, and mlogit \cite{mlogit}.
-
-The Julia language \cite{Bezanson_Edelman_Karpinski_Shah_2017} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks.
 
@@
 For example, \textit{coef} will extract the parameter estimates from any object that implements the API.
-The full API include model statistics such as: coefficient of determination (or adjusted), information criteria statistics such as AIC/BIC (and corrected), statistics about the model fitness such as deviance, log-likelihood, and usual queries such as point estimates, variance covariance estimates, standard errors, confidence intervals, degrees of freedom (or residual degrees of freedom), etc.
+The full API include model statistics such as: coefficient of determination (or adjusted), information criteria statistics such as AIC/BIC (and corrected), statistics about the model fitness such as deviance, log-likelihood, and usual queries such as point estimates, variance covariance estimates, standard errors, confidence intervals, degrees of freedom (or residual degrees of freedom).
 Lastly, several accessors are available for fitted values, response, model matrix, information matrix, leverage values, error components, etc.
@@
 
-Software analysis should always include diagnostics and tools to make it easier for dissemination.
-Many tests and diagnostics are applicable to a wide set of implementations.
-The best manner to make these available and for these to ``play nicely'' with one another is to have an effective API.
-Sadly, the Julia ecosystem has yet to experience wide adoption of this pattern.
-For example, packages might need to access components for computing a test or providing some estimates such as variance covariance estimates.
-The test might include components such as the residual degrees of freedom, the information matrix, residuals, and score.
-Currently, some packages rely on accessing internal components specific to those implementations rather than an implementation agnostic interface.
-A common public API would also allow to catch context specific instances of improper behavior.
+The decision to adhere to a common API has various benefits.
+For example, being able to interact and query models consistently enables packages that enhance the experience providing features such as diagnostics (i.e., statistical tests, plots) or convenience tools for dissemination such as \LaTeX\ code for results.
+Currently, the ecosystem still demands certain functionality to rely on internals which forces code to be less generalizable (e.g., CovarianceMatrices.jl only supports GLM models and relies on internals rather than a common API).
 
-Various decisions are software specific with asymptotic justification, but significant finite-sample consequences.
-Software may differ on whether to report statistics using finite-sample statistics (t-distribution, F-distribution) or asymptotic equivalent counterparts (Normal, Chi squared).
-These tend to have negligible effect in most applications, but other decisions such as degrees of freedom may have larger consequences.
-For example, software may differs on how it computes the degrees of freedom for instrumental variables or absorbed variables depending on the context (e.g., main regression or auxiliary regression for estimating error components).
+Econometrics.jl has as a goal to make opinionated decisions after careful consideration.
+Consider for example whether to report statistics using finite-sample statistics (t-distribution, F-distribution) or asymptotic equivalent counterparts (Normal, Chi squared).
+These tend to have negligible effects in most applications, but other decisions such as degrees of freedom may have larger consequences.
+One case is how software computes the degrees of freedom for instrumental variables or absorbed variables depending on the context (e.g., main regression or auxiliary regression for estimating error components).
 Refinements and robustness checks can also contribute to a better analysis such as verifying gaps for time variant operations such as in first-difference or purging singletons and other degree of freedom adjustments \cite{Singletons}.

### 2019-08-13 src/formula.jl
Minor improvements to docs
* Improvements to docs
* Public API

@@ -1,7 +1,7 @@
 """
     absorb
 
-Dummy function for constructing the FunctionTerm{typeof(absorb)} used in decompose.
+Function for constructing the `FunctionTerm{typeof(absorb)}` used in decompose.
 """
 function absorb end
 """

### 2019-08-13 dev/search_index.js
build based on 0ad47ae

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"getting_started/#Getting-Started-1","page":"Getting Started","title":"Getting Started","text":"","category":"section"},{"location":"getting_started/#Installation-1","page":"Getting Started","title":"Installation","text":"","category":"section"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"Econometrics.jl is registered with the Julia's General registry.","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"For installing the package, users can use Julia's package manager.","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"using Pkg; Pkg.add(\"Econometrics\") # one alternative\n]add Econometrics # same as the line above","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"The package manager will automatically resolve which release version for Econometrics.jl is compatible with the environment in use.","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"The package manager allows for other experiences such as downloading the development version of the package through","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"]add Econometrics#master","category":"page"},{"location":"getting_started/#Data-1","page":"Getting Started","title":"Data","text":"","category":"section"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"Econometrics.jl relies on users being able to pass in data for estimating the various models. This package allows for data to be passed through any tabular representation that implements the Tables.jl API. For example, a DataFrame from DataFrames.jl is a common solution for in-memory tabular data that implements the Tables.jl API.","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"The second assumption Econometrics.jl makes about the data is that categorical data uses the CategoricalArrays.jl representations (i.e., AbstractCategoricalVector, CategoricalValue).","category":"page"},{"location":"getting_started/#","page":"Getting Started","title":"Getting Started","text":"Lastly, the package currently assumes in-memory data.","category":"page"},{"location":"getting_started/#Specifying-a-Mo
[…]

### 2019-08-13 paper/paper.tex
Updates from Overleaf
- Added brief explanation of the `fit` method - Added a note about how to install the package

@@
 
+The syntax to estimate a model follows the StatsBase API which provides two methods for building and estimating models (i.e., \textit{fit} and \textit{fit!}).
+The \textit{fit} approach takes (1) an estimator, (2) a model formula, (3) data, and additional arguments depending on the model.
+\textit{EconometricModel} is the generic estimator which dispatches to continuous, nominal or ordinal response models automatically based on the type of the response.
+Other estimators are available and the following figures illustrate some of the use cases.
+
 \begin{figure}[hbpt]
@@
 Econometrics.jl is ISC licensed and available at the GitHub repository.
+The package is registered in the official Julia registry (General); as such it can be installed using the Julia package manager.
 

### 2019-08-19 src/main.jl
Fix polr
Fixes polr estimator
- Bug when the number of parameters /outcomes differed.

@@ -59,7 +59,7 @@ mutable struct EconometricModel{E<:ModelEstimator,
         if isa(estimator, Union{NominalResponse, OrdinalResponse})
             @unpack categories = estimator
             y = [ findfirst(isequal(x), categories) for x ∈ y ]
-            @assert length(categories) > 2
+            @assert length(categories) > 1
         end
         if isa(estimator, NominalResponse)
             ŷ = zeros(0, 0)

### 2019-08-19 src/solvers.jl
Fix polr (#19)
Fixes polr estimator
- Bug when the number of parameters /outcomes differed.

@@ -261,7 +261,7 @@ Solves a proportional odds logistic regression.
     m, n = size(X)
     xs = 1:n
     ks = length(categories) - 1
-    ζs = ks:(ks + n)
+    ζs = n + 1:(n + ks)
     δ₀ = mapreduce(x -> (1:ks .== x - 1)', vcat, y)
     δ₁ = mapreduce(x -> (1:ks .== x)', vcat, y)
     η = Vector{Union{Float64,Dual}}(undef, m)
@@ -277,7 +277,7 @@ Solves a proportional odds logistic regression.
     θ₁ = ones(ks)
     function f(β)
       η .= X * β[xs]
-      ζ[2:end - 1] .= cumsum(vcat(β[size(X, 2) + 1], exp.(β[size(X, 2) + 2:end])))
+      ζ[2:end - 1] .= cumsum(vcat(β[n + 1], exp.(β[n + 2:end])))
       Y₀ .= max.(-100, ζ[y] - η)
       Y₁ .= min.(100, ζ[y₁] - η)
       F₀ .= cdf.(Logistic(), Y₀)
@@ -286,8 +286,7 @@ Solves a proportional odds logistic regression.
       -sum(w * log(p) for (w, p) ∈ zip(wts, pr))
     end
     function g!(G, β)
-      θ = β[size(X, 2) + 1:end]
-      ζ[2:end - 1] .= cumsum(vcat(θ[1], exp.(θ[2:end])))
+      ζ[2:end - 1] .= cumsum(vcat(β[n + 1], exp.(β[n + 2:end])))
       η .= X * β[xs]
       Y₀ .= max.(-100, ζ[y] - η)
       Y₁ .= min.(100, ζ[y₁] - η)
@@ -298,7 +297,7 @@ Solves a proportional odds logistic regression.
       f₁ .= pdf.(Logistic(), Y₁)
       G[xs] .= X' * (wts .* (f₁ .- f₀) ./ pr)
       g2 = - (δ₁ .* f₁ .- δ₀ .* f₀)' * (wts ./ pr)
-      θ₁[2:end] .= exp.(θ[2:end])
+      θ₁[2:end] .= exp.(β[ζs[2:end]])
       G[ζs] .= diagm((d => θ₁[1:ks - d] for d ∈ 0:ks - 1)...) * g2
     end
     β₀ = vcat(zero(xs), log.(1:ks))
[…]

### 2019-08-19 test/runtests.jl

@@ -234,16 +234,33 @@ end
   	β, V, σ = coef(model), vcov(model), stderror(model)
   	@test β ≈ [ 0.009437926, -0.015143049, -0.103911316,
                -2.92391240,  -1.549266200, -0.298963900, 0.6698249] rtol = 1e-4
-	@test V ≈ [ 0.00000646 -0.0000007000  0.000013250 0.00031473	0.0003161358 0.000321276 0.0003270734
-               -0.00000070  0.0071633800 -0.000184930 0.00294759	0.0029647442 0.002995366 0.0029904485
-                0.00001325 -0.0001849300  0.000618730 0.00288365	0.0028548209 0.002791361 0.0027318928
-                0.00031473  0.0029475900  0.002883650 0.03684071	0.0289239290 0.026986237 0.026498765
-                0.00031614  0.0029647400  0.002854820 0.02892393	0.0293971651 0.027160433 0.0266006675
-                0.000321276 0.0029953660  0.002791361 0.02698623	0.0271604331 0.027860143 0.0270590982
-                0.0003270734 0.002990448  0.002731893 0.02649876	0.0266006675 0.027059098 0.0281002038
+	@test V ≈ [ 0.00000646  -0.0000007000  0.000013250  0.00031473  0.0003161358  0.000321276  0.0003270734
+               -0.00000070   0.0071633800 -0.000184930  0.00294759  0.0029647442  0.002995366  0.0029904485
+                0.00001325  -0.0001849300  0.000618730  0.00288365  0.0028548209  0.002791361  0.0027318928
+                0.00031473   0.0029475900  0.002883650  0.03684071  0.0289239290  0.026986237  0.026498765
+                0.00031614   0.0029647400  0.002854820  0.02892393  0.0293971651  0.027160433  0.0266006675
+                0.000321276  0.0029953660  0.002791361  0.02698623  0.0271604331  0.027860143  0.0270590982
+                0.0003270734 0.002990448   0.002731893  0.02649876  0.0266006675  0.027059098  0.0281002038
               ] rtol = 1e-3
     @test σ ≈ [0.002540789, 0.084636770, 0.024874381,
                0.191939349, 0.171456015, 0.166913580, 0.167631154] rtol = 1e-4
+	data = data[data.RecParks .≠ 5,:]
+	model = fit(EconometricModel,
+              	@formula(RecParks ~ Age + Sex + Schooling),
[…]

### 2019-08-19 src/main.jl
Fix docstring of EconometricModel
Outdated docstring.

@@ -1,10 +1,12 @@
 """
-    EconometricModel(f::FormulaTerm, data;
-                     contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}},
-                     weights::Union{Nothing,Symbol} = nothing,
+    EconometricModel(estimator::Type{<:Union{EconometricModel,ModelEstimator}},
+                     f::FormulaTerm,
+                     data;
+                     contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}}(),
+                     wts::Union{Nothing,Symbol} = nothing,
                      panel::Union{Nothing,Symbol} = nothing,
                      time::Union{Nothing,Symbol} = nothing,
-                     estimator::ModelEstimator = ModelEstimator)
+                     vce::VCE = OIM)
 
 Formula has syntax:
 

### 2019-08-19 dev/search_index.js
build based on 1fa3a0f

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"public_api/#Public-API-1","page":"Public API","title":"Public API","text":"","category":"section"},{"location":"public_api/#","page":"Public API","title":"Public API","text":"absorb\nEconometricModel\nBetweenEstimator\nRandomEffectsEstimator\nEconometrics.VCE","category":"page"},{"location":"public_api/#Econometrics.absorb","page":"Public API","title":"Econometrics.absorb","text":"absorb\n\nFunction for constructing the FunctionTerm{typeof(absorb)} used in decompose.\n\n\n\n\n\n","category":"function"},{"location":"public_api/#Econometrics.EconometricModel","page":"Public API","title":"Econometrics.EconometricModel","text":"EconometricModel(f::FormulaTerm, data;\n                 contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}},\n                 weights::Union{Nothing,Symbol} = nothing,\n                 panel::Union{Nothing,Symbol} = nothing,\n                 time::Union{Nothing,Symbol} = nothing,\n                 estimator::ModelEstimator = ModelEstimator)\n\nFormula has syntax:\n\n@formula(response ~ exogenous + (endogenous ~ instruments) + absorb(highdimscontrols))\n\nData must implement the Tables.jl API and use CategoricalArrays (CategoricalVector)\n\nWeights are taken as StatsBase.FrequencyWeights\n\nPanel and time indicators are used for longitudinal estimators\n\nExamples\n\nmodel = fit(EconometricModel, formula, data, kwargs...)\nmodel = fit(BetweenEstimator, formula, data, panel = :panel, kwargs...)\nmodel = fit(RandomEffectsEstimator, formula, data, panel = :panel, time = :time, kwargs...)\n\n\n\n\n\n","category":"type"},{"location":"public_api/#Econometrics.BetweenEstimator","page":"Public API","title":"Econometrics.BetweenEstimator","text":"BetweenEstimator(effect::Symbol,\n                 groups::Vector{Vector{Int}}) <: LinearModelEstimators\n\nContinuous response estimator collapsing a dimension in a longitudinal setting.\n\n\n\n\n\n","category":"type"},{"location":"public_api/#Econometrics.RandomEffectsEstimator","page":"Public API","title":"Econometrics.RandomEffectsEstimator","text":"RandomEffectsEstimator(pid::Tupl
[…]

### 2019-08-20 src/Econometrics.jl
Support for LTS version
Add compat for ismissing/isnothing

@@ -34,6 +34,15 @@ module Econometrics
                       meanresponse, modelmatrix, leverage, residuals, predict,
                       predict!, dof_residual, RegressionModel, params
     import StatsModels: hasintercept, implicit_intercept
+    # Compat
+    if !@isdefined(isnothing)
+        isnothing(::Any) = false
+        isnothing(::Nothing) = true
+    end
+    if !@isdefined(ismissing)
+        isnothing(::Any) = false
+        isnothing(::Missing) = true
+    end
     foreach(file -> include(joinpath(dirname(@__DIR__), "src", "$file.jl")),
             ["structs", "transformations", "formula", "main", "solvers", "statsbase", "wald"])
     export @formula, DummyCoding, aic, aicc, bic, coef, coefnames,

### 2019-08-24 paper/paper.tex
Clean up of ref.bib
- Clean up the ref.bib to exclude nocite
- Added note about chapter 3 of dissertation

@@
 \urlstyle{same}
+
+\DeclareMathOperator{\HadamardProduct}{.*}
 
@@
 Singular value decomposition may also be used, but it is rare as the computational complexity is significantly higher.
-In the case of the QR decomposition the solution method comes down to, transforming the model matrix and the response by row-wise multiplying them by the square root of the weights.
-Afterwards, the factorization is used to solve the system of equations using the appropriate method.
+In the case of the QR decomposition the solution method comes down to, transforming the model matrix and the response by row-wise multiplying them by the square root of the weights.\footnote{The row-wise Hadamard product is used in equation \ref{QR} as ($\HadamardProduct$).} Afterwards, the factorization is used to solve the system of equations using the appropriate method.
 In the case of a QR decomposition, $R$ is an upper triangular matrix which enables back substitution to obtain the solution efficiently without matrix inversion.
 However, a Cholesky decomposition would still be required if the information matrix is desired.
-The solution method with QR decomposition is delineated in equation \ref{QR}.\footnote{The (\textbackslash)\ refers to multiplication of $b$ by the inverse of $A$ on the left.}
+The solution method with QR decomposition is delineated in equation \ref{QR}.\footnote{The (\textbackslash)\ is a linear solver operator, such that $x = A \backslash b => Ax = b$.}
 
@@
 \begin{split}
-	\tilde{X} = X .* \sqrt{w} \\
-	\tilde{y} = y .* \sqrt{w} \\
+	\tilde{X} = X \HadamardProduct \sqrt{w} \\
+	\tilde{y} = y \HadamardProduct \sqrt{w} \\
 	QR = \tilde{X} \\
@@
 There are several methods to obtain a suitable alternative regression and these are not unique.
-Stata's module reghdfe \cite{reghdfe} presents several approaches to solving these problem including specialized methods in certain applications.
-Some implementations include Stata module reghdfe and the FixedEffects.jl package.
+Stata's module reghdfe \cite{reghdfe} presents several approaches to solving these problems including specialized methods in certain applications.
+Some implementations include Stata module reghdfe and the FixedEffectsModels.jl \cite{FixedEffectModels.jl} package.
 The two most common approaches are solving for the residuals through a sparse least-squares problems such as with LSMR \cite{LSMR} or using some variant for the method of alternating projections.
@@
 
-\subsection{First-Difference}
+\subsection{First-Difference Estimator}
 
@@
 
-The log-likelihood function has the same form as the general form for computing the cost associated with a categorical distribution and predicted probability for realization. More specific,
+The log-likelihood ($\ell$) function has the same form as the general form for computing the cost associated with a categorical distribution and predicted probability for realization. More specific,
 \begin{equation}
-	\ell \ell = \sum_{i = 1}^{m} \sum_{k}^{K} \mathbbm{1}\left(y_{i} = k\right) \ln\left[F\left(\alpha_{k + 1} - \eta\right) - F\left(\alpha_{k} - \eta\right)\right]
+	\ell = \sum_{i = 1}^{m} \sum_{k}^{K} \mathbbm{1}\left(y_{i} = k\right) \ln\left[F\left(\alpha_{k + 1} - \eta\right) - F\left(\alpha_{k} - \eta\right)\right]
 \end{equation}
@@
 The usual pipeline for regression analysis involves (1) accessing data (I/O), (2) obtaining a tabular data representation, (3) data wrangling, and (4) employing regression analysis tools.
-The Julia ecosystem follows this canonical pipeline.
-The following sections provides an overview of the pipeline available in Julia.
+The following sections provides an overview of the pipeline available in Julia provided by the Julia statistics and data ecosystems.
 
@@
 
-StatsBase.jl builds on top of Statistics.jl (standard library) to provide additional statistical functionality.
+StatsBase.jl \cite{StatsBase.jl} builds on top of Statistics.jl (standard library) to provide additional statistical functionality.
 One which includes the abstraction for Statistical Models (and Regression models which inherits from the former).
@@
 
-Tables.jl provide an interface for tabular data.
+Tables.jl \cite{Tables.jl} provide an interface for tabular data.
 This API allows users to choose from various solutions the tabular data implementation of their choosing without having to worry that their choice will limit potential functionality.
-Many tabular implementations such as DataFrames.jl provide robust functionality to many routines such as handling categorical features, dates/time, missing values, reshaping data, split/apply operations, and others.
+Many tabular implementations such as DataFrames.jl \cite{DataFrames.jl} provide robust functionality to many routines such as handling categorical features, dates/time, missing values, reshaping data, split/apply operations, and others.
 Users need not to worry about any I/O issues as a rich array of options exist for importing and exporting across different file formats such as delimiter-separated values, JSON, Feather, HDF5, MATLAB, Stata, SPSS, SAS, and R.
 
-StatsModels.jl is a package that provides the means to go from data to model terms.
+StatsModels.jl \cite{StatsModels.jl} is a package that provides the means to go from data to model terms.
 It provides the formulae language (e.g., similar to R's formulae syntax).
@@
 
-The regression analysis ecosystem in Julia has GLM.jl as its flagship.
+The regression analysis ecosystem in Julia has GLM.jl \cite{GLM.jl} as its flagship.
 GLM.jl provides the typical functionality for fitting generalized linear models through Fisher scoring.
 This includes linear models, Poisson/Negative Binomial, Logit/Probit, and other non-canonical link models.
-CovarianceMatrices.jl provides various variance covariance estimators for GLM.jl models à la R's
+CovarianceMatrices.jl \cite{CovarianceMatrices.jl} provides various variance covariance estimators for GLM.jl models à la R's
 sandwich package.
@@
 
-\subsection{Design Decisions}
+\subsection{Should Software be Dummy-Proof?}
 
@@
 Econometrics.jl adopts the best practices standards for open-source statistical software.
-These include adhering to semantic versioning (semver) for descriptive versioning, continuous integration for development, software validation through a comprehensive code coverage and test suite, and lastly online hosted documentation for the public API.
+These include adhering to semantic versioning (semver) for descriptive versioning, continuous integration for development, software validation through a comprehensive code coverage and test suite, and lastly online hosted documentation for the public API.\footnote{\href{https://nosferican.github.io/Econometrics.jl/stable}{https://nosferican.github.io/Econometrics.jl/stable}}
 
@@
 
+I would also like to thank Hisam Sabouni for useful feedback during the development of the project and at an earlier draft of the article \cite{JBSC2019} and Jeffrey Wooldridge for guidance in the programming of the estimators.
+
 \input{bib.tex}

### 2019-08-28 paper/paper.tex
Added Survival.jl manual reference.
Updates from Overleaf

@@
 sandwich package.
-LinearMixedModels.jl \cite{LinearMixedModels} extends GLM.jl for mixed-effects models.
+MixedModels.jl \cite{MixedModels.jl} extends GLM.jl for mixed-effects models.
 FixedEffectModels.jl provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la reghdfe.
-Survival.jl provides a series of estimators for duration models.
+Survival.jl \cite{Survival.jl} provides a series of estimators for duration models.
 Two major gaps in the ecosystem include estimating nominal and ordinal response models (i.e., discrete choice) with more than two alternatives and support for longitudinal estimators.
@@
 
-The syntax to estimate a model follows the StatsBase API which provides two methods for building and estimating models (i.e., \textit{fit} and \textit{fit!}).
+The syntax to estimate a model follows the StatsBase API which provides a method for building and estimating models (i.e., \textit{fit}).
 The \textit{fit} approach takes (1) an estimator, (2) a model formula, (3) data, and additional arguments depending on the model.
@@
 Other estimators are available and the following figures illustrate some of the use cases.
+
+The fixed effects model or within estimator can be estimated as in figure \vref{withinmodel} which a two-ways fixed effects model (i.e., fixed effects for panel and time dimensions).
+Table \vref{withinres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.
+
+The random effects model can be estimated as in figure \vref{random} which shows estimating a random effects model with instrumental variables.
+Table \vref{xtregres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata's reghdfe module, and R's plm package.
+
+The sysdsn1 Stata example health insurance data set is used to illustrate the multinominal logistic regression when the response is nominal as seen in figure \vref{mlogit}.
+A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl and Stata is shown in table \vref{mlogitres}.
+
+The fullauto Stata example automobile models data set is used to illustrate the proportional ordinal logistic regression when the response is ordinal as seen in figure \vref{ologit}.
+A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl, Stata, and R's MASS is shown in table \vref{ologitres}.
 
@@
 
-The fixed effects model or within estimator can be estimated as in figure \vref{withinmodel} which a two-ways fixed effects model (i.e., fixed effects for panel and time dimensions).
-Table \vref{withinres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.
-
 \begin{figure}[hbpt]
@@
 \end{figure}
-
-\newpage
-
-The random effects model can be estimated as in figure \vref{random} which shows estimating a random effects model with instrumental variables.
-Table \vref{xtregres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata's reghdfe module, and R's plm package.
 
@@
 
-The sysdsn1 Stata example health insurance data set is used to illustrate the multinominal logistic regression when the response is nominal as seen in figure \vref{mlogit}.
-A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl and Stata is shown in table \vref{mlogitres}.
-
 \begin{figure}[hbpt]
@@
 \end{figure}
-
-The fullauto Stata example automobile models data set is used to illustrate the proportional ordinal logistic regression when the response is ordinal as seen in figure \vref{ologit}.
-A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl, Stata, and R's MASS is shown in table \vref{ologitres}.
 

### 2019-08-28 v0.2.2/search_index.js
build based on 41ddabe

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"public_api/#Public-API-1","page":"Public API","title":"Public API","text":"","category":"section"},{"location":"public_api/#","page":"Public API","title":"Public API","text":"absorb\nEconometricModel\nBetweenEstimator\nRandomEffectsEstimator\nEconometrics.VCE","category":"page"},{"location":"public_api/#Econometrics.absorb","page":"Public API","title":"Econometrics.absorb","text":"absorb\n\nFunction for constructing the FunctionTerm{typeof(absorb)} used in decompose.\n\n\n\n\n\n","category":"function"},{"location":"public_api/#Econometrics.EconometricModel","page":"Public API","title":"Econometrics.EconometricModel","text":"EconometricModel(estimator::Type{<:Union{EconometricModel,ModelEstimator}},\n                 f::FormulaTerm,\n                 data;\n                 contrasts::Dict{Symbol} = Dict{Symbol,Union{<:AbstractContrasts,<:AbstractTerm}}(),\n                 wts::Union{Nothing,Symbol} = nothing,\n                 panel::Union{Nothing,Symbol} = nothing,\n                 time::Union{Nothing,Symbol} = nothing,\n                 vce::VCE = OIM)\n\nFormula has syntax:\n\n@formula(response ~ exogenous + (endogenous ~ instruments) + absorb(highdimscontrols))\n\nData must implement the Tables.jl API and use CategoricalArrays (CategoricalVector)\n\nWeights are taken as StatsBase.FrequencyWeights\n\nPanel and time indicators are used for longitudinal estimators\n\nExamples\n\nmodel = fit(EconometricModel, formula, data, kwargs...)\nmodel = fit(BetweenEstimator, formula, data, panel = :panel, kwargs...)\nmodel = fit(RandomEffectsEstimator, formula, data, panel = :panel, time = :time, kwargs...)\n\n\n\n\n\n","category":"type"},{"location":"public_api/#Econometrics.BetweenEstimator","page":"Public API","title":"Econometrics.BetweenEstimator","text":"BetweenEstimator(effect::Symbol,\n                 groups::Vector{Vector{Int}}) <: LinearModelEstimators\n\nContinuous response estimator collapsing a dimension in a longitudinal setting.\n\n\n\n\n\n","category":"type"},{"location":"public_api/#Econometrics.RandomEffectsEstimator","page":"Public API","title":"Econometrics.RandomEff
[…]
